### 2015-05-02 draft.tex
first commit

\title{Survival Set Connectivity}
\author{
  Fermi Ma \and
  Erik Waingarten
}
\date{\today}

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}

\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}

\begin{document}
\maketitle

\section{Introduction}

We analyze the following problem, which we call Survival Set Connectivity (SSC): 
\begin{quote}
\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
\end{quote}

Note that this problem generalizes the common connectivity problems. The question of whether there are $k$ connections between $s$ and $t$ sets only one pair $(S_1, T_1)$ where $S_1 = \{ s \}$ and $T_i = \{ t \}$.

[ GIVE MORE EXAMPLES HERE ]

As with many of these kinds of problems, SSC is $\mathsf{NP}$-hard. The common route taken in 6.856 has been to find polynomial time algorithms for approximations; however, in the case with SSC, it is $\mathsf{NP}$-hard to achieve a polylogarithmic approximation.

Another possible approach is therefore to relax the question. Instead of requiring at least $k$ edge-disjoint paths, we will allow some sets to have less than $k$ paths, but not too much less. We will present an approximation algorithm which outputs a subgraph of cost $O(polylog(n))$ times the optimum such that for each $(S_i, T_i)$ pairs, there are at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths between $S_i$ and $T_i$.

The approximation algorithm will follow the usual approach to approximation algorithms of this kind. We will first write the problem as an integer linear program, we solve the linear programming relaxation, and then we round the solution.

The analysis will be slightly different from the analysis shown in class. Usually, our randomized algorithm will return a feasible solution to the problem, and our analysis work is mostly to bound the cost. This was the case with max-sat, set-cover, and multi-commodity flows. In our case, we will show that the rounded solution will be close to the optimal, but we will work to show that the rounded solution is feasible.

\section{Linear Programming Formulation}

We can formulate a cut-based integer linear program for SSC. We will have a variable
\begin{align}
 x_e &= \left\{ \begin{array}{cc} 1 & e \in H \\
                                  0 & \text{ otherwise } \end{array} \right.
\end{align}
So $H$ will be the subgraph consisting of the edges $e$ where $x_e = 1$. \\ \\
SSC-LP:
\begin{align}
\min & \sum c(x) x_e  \\
\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{ where } S_i \subset S, T_i \subset V - S, \delta(S) \text{ is the edges of the $S$ cut }
\end{align}
This cut-based integer linear program finds exactly $H$. To see why the constraints ensure that each $(S_i, T_i)$ pair has at least $k$ edge disjoint paths, we can look at the cuts corresponding to $S_i$ and $T_i$. First, we let $S = S_i$, then there are $k$ outgoing edges. We can choose to include one more node to $S$, following a particular outgoing edge of the cut in $H$. We can continue doing this until we reach $T_i$. This will trace out a path between $S_i$ and $T_i$. If we do this for each edge, and then we do this for each $(S_i, T_i)$ pair, we can confirm that there are in fact $k$ edge-disjoint paths between each $(S_i, T_i)$ pair.

There is one caveat that has not been addressed. We have exponentially many constraints! Since there can be exponentially many set $S$ with $S_i \subset S$ and $T_i \subset V - S$. We solve this with a similar idea to semi-definite programming, by giving a separation oracle which runs in polynomial time.

The separation oracle will just compute the minimum $S_i, T_i$ cut in the graph. What we can do is contract $S_i$ and $T_i$ to single edges, and then compute the min-cut in the remaining graph. If there is a min-cut of size less than $k$, then that cut will correspond to a violating contraint. If the min-cut has size at least $k$, then all cuts have size at least $k$, so we have satisfied the constraints.

The linear programming relaxation to the above program will be the first step of the algorithm. The remaining work will be rounding the fractional solution to an integral solution and satisfy the constraints.

\section{Tree Embeddings}

The next tool we will need are tree embeddings. We have seen metric embeddings in class. Basically, we had a desired type of object $O$ (in the case of cuts, we had a metric space corresponding to a cut) what we did was come up with a metric space $(X, d)$ and a map $f: (X, d) \rightarrow O$ such that the map satisfied certain properties on the distances.

Here we will have a similar goal. We want to understand minimum cost weighted graphs, but since analyzing them is hard, we instead study minimum cost weighted trees, and then we map the trees back to the graphs.

\begin{definition}
A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup E$ such that
\begin{align}
\text{map}(V_t) &\subset V \\
\text{map}(E_t) &\subset E
\end{align}
In other words, vertices map to vertices and edges map to edges. We will usually refer to an embedding as $(T, y, \text{map})$. 
\end{definition}

[ Give some pictures of  tree embeddings here ]

\subsection{Racke Tree Black Box}

\subsection{RoundGKR Black Box}

\section{Algorithm}

\subsection{Analysis}

\section{Conclusion}

\subsection{Open Problems}

\end{document}

### 2015-05-06 draft.tex
added examples and finish drafting racketrees

@@
 \usepackage{amsfonts}
+\usepackage{graphicx}
 
@@
 \newtheorem{definition}{Definition}
+\newtheorem{lemma}{Lemma}
 
@@
 \begin{definition}
-A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup E$ such that
+A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
 \begin{align}
@@
 
-[ Give some pictures of  tree embeddings here ]
+\subsection{Racke Tree Black Box}
 
-\subsection{Racke Tree Black Box}
+We will use a particular type of tree embedding which will allow us to paths in the tree to paths in the graph.
+
+\begin{definition}
+For a given graph $G = (V, E)$, a Racke Tree is a tree embedding of $G$, $(T, y, \text{map})$ such that:
+\begin{enumerate}
+\item $\text{map}$ restricted to the leafs of $T$ is a bijection with the vertices of $G$.
+\item For each edge $e \in E_t$ joining $u$ and $v$, $\text{map}(e)$ is a path joining nodes $\text{map}(u)$ and $\text{map}(v)$.
+\item For some edge $e \in E_t$, $y_e$ (the cost of the edge) is a special quantity.
+Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$.
+Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
+\begin{align}
+y_e &= \sum_{e' \in \delta(S)} x_e
+\end{align}
+\end{enumerate}
+\end{definition}
+
+\begin{figure}
+\centering
+\label{fig:rackecut}
+\includegraphics[width=0.5\linewidth]{Rackecut.pdf}
+\caption{Racke tree cut induced by an edge in the tree.}
+\end{figure}
+
+Having made these definition, we can refer to the inverse $\text{map}^{-1}$ in the obvious manner.
+$\text{map}^{-1}$ on a vertex will map to the corresponding leaf, and $\text{map}^{-1}$ on an edge in the graph will map to all edges in the tree whose paths contain that edge.
+
+\begin{definition}
+Given a Racke tree, the load on an edge of the graph $e \in E$ is
+\begin{align}
+load(e) &= \sum_{f \in \text{map}^{-1}} y_f
+\end{align}
+The relative load, $rload(e) = \dfrac{load(e)}{x_e}$. 
+\end{definition}
+
+Figure~\ref{fig:racketree} gives an example of a Racke tree with the mapping.
+Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices.
+This gives us a simple way to map flows from Racke trees to the graph and vice-versa.
+
+In particular, if we have a multicommodity flow $\{ f_i \}$ on the graph, then we can easily map into a multicommodity flow on the Racke tree.
+If there is a flow $f_i$ from $s_i$ to $t_i$, then we find leaves $s_i^{T}=\text{map}^{-1}(s_i)$ and $t_i^T\text{map}^{-1}(t_i)$ and route $f_i$ units of flow through the unique path from $s_i$ to $t_i$.
+
+For obtaining a flow on the graph given one on the Racke tree, if $f_i^T(e)$ is the flow of commodity $i$ on the tree on $e \in E_t$, then we route $f_i^T(e)$ units of flow down the path given by $\text{map}(e)$.
+
+\begin{figure}
+\label{fig:racketree}
+\centering
+\includegraphics[width=\linewidth]{Rackeembeddinggraph.pdf}
+\caption{Example Racke Tree where red nodes are mapped and edge maps to a path.}
+\end{figure}
+
+There are some crucial properties of Racke trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to [CITE] for the proofs.
+
+\begin{lemma}
+If we have a graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$ and a Racke tree $(T, y, \text{map})$.
+A multicommodity flow on $G$, $\{ f_i \}$, maps directly to a multicommodity flow on the tree which is also feasible.
+Likewise, a multicommodity flow on $T$ maps directly into a multicommodity flow on the graph, with the small caveat that we must multiply the capacity of the edge by the relative load.
+\end{lemma}
+
+[ EXPLAIN HOW TO MAP FLOWS ]
+
+\begin{lemma}
+For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$, we can sample efficiently from Racke trees of $G$, such that 
+\begin{align}
+\max_{e \in E} \textbf{E}[rload(e)] &\leq \alpha = O(\log n) 
+\end{align}
+\end{lemma}
+
+\begin{lemma}
+The height of the trees sampled is $O(\log nC)$, where $C$ is the ratio of the largest to smallest capacity in $G$. In our cases, the height will always be $O(\log n)$. 
+\end{lemma}
 

### 2015-05-06 draft.tex
changed introduction a little bit

@@
-\title{Survival Set Connectivity}
+\title{Survivable Set Connectivity}
 \author{
-  Fermi Ma \and
-  Erik Waingarten
+ by Fermi Ma and Erik Waingarten
 }
@@
 
-We analyze the following problem, which we call Survival Set Connectivity (SSC): 
+In this paper, we analyze the problem of Survivable Set Connectivity (SSC), a generalization of the classical Set Connectivity problem. Set connectivity is formulated as:
+\begin{quote}
+\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$. \\
+\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there is a path between $S_i$ and $T_i$ for each $i$. 
+\end{quote}
+In SSC, the problem is modified so that each pair of sets $(S_i,T_i)$ must be connected by $k_i$ paths, instead of just 1. More formally, the problem is:
+
 \begin{quote}

### 2015-05-06 draft.tex
added RoundedGKR draft

--- 2015-05-06 draft.tex
@@
 \begin{quote}
-\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
+\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
 \textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
@@
 \begin{definition}
-A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
+A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}^{\geq 0}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
 \begin{align}
@@
 \begin{align}
-load(e) &= \sum_{f \in \text{map}^{-1}} y_f
+load(e) &= \sum_{f \in \text{map}^{-1}(e)} y_f
 \end{align}
@@
 \begin{lemma}
-If we have a graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$ and a Racke tree $(T, y, \text{map})$.
+\label{lem:mapflows}
+If we have a graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}^{\geq 0}$ and a Racke tree $(T, y, \text{map})$.
 A multicommodity flow on $G$, $\{ f_i \}$, maps directly to a multicommodity flow on the tree which is also feasible.
@@
 
-[ EXPLAIN HOW TO MAP FLOWS ]
-
 \begin{lemma}
-For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$, we can sample efficiently from Racke trees of $G$, such that 
+\label{lem:rload}
+For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}^{\geq 0}$, we can sample efficiently from Racke trees of $G$, such that 
 \begin{align}
@@
 \begin{lemma}
+\label{thm:height}
 The height of the trees sampled is $O(\log nC)$, where $C$ is the ratio of the largest to smallest capacity in $G$. In our cases, the height will always be $O(\log n)$. 
@@
 \subsection{RoundGKR Black Box}
+
+The RoundGKR algorithm is an algorithm to rounding algorithm used for the Group Steiner Tree problem. We first describe the problem and give the algorithm. \\
+
+Group Steiner Tree:
+\begin{quote}
+\textbf{Input}: A rooted tree $T = (V_t, E_t)$ at $r$ with costs $c: E_t \rightarrow \mathbb{R}^{\geq 0}$ as well as subsets of vertices $\{ T_i \}$. \\
+\textbf{Output}: A minimum cost subtree $H \subset T$ with a path from $r$ to $t_i$ for some $t \in T_i$ for all $i$.
+\end{quote}
+
+A similar linear program produces a fractional solution, and the algorith RoundGKR is a way of rounding the solution back.
+The optimum to the linear program will be a set of values for each edge $y_e \in [0, 1]$.
+Since we are in a tree setting and we are looking for paths from the root, we can assume that $y_{p(e)} \geq y_e$ (parent edges are always greater).
+
+The RoundGKR is simple, it starts at the root and makes its way down the tree as its being built.
+It includes the edge $e$ in the subtree with probability $\frac{y_e}{y_{p(e)}}$.
+A simple inductive argment shows that an edge $e$ is chosen with probability $y_e$.
+This is because $Pr[\text{include $e$}] = Pr[\text{include $e$ $|$ include $p(e)$}]*Pr[\text{include $p(e)$}] = y_e$ (if we don't include $p(e)$, then we don't include $e$.
+
+The important property of the algorithm can be summarized in the following lemma, whose proof we refer to [CITE].
+
+\begin{lemma}
+\label{lem:findpath}
+Suppose that $T = (V_t, E_t)$ support a flow of at least $1$ from $T_i$ to the root $r$ without the edges $F_t$.
+Then the RoundGKR returns a solution with a path in $T$ from $T_i$ to $r$ without using $F_t$ with probability at least $\Omega(\frac{1}{\log n})$.
+\end{lemma}
+
+We will rely on this lemma heavily.
+In fact, since we need $\Omega(\frac{k}{\log n})$ edge-disjoint paths, we will argue that if we let $F_t$ be any set of at most $\Omega(\frac{k}{\log n})$ edges, then we still have a path, and therefore, we have $\Omega(\frac{k}{\log n})$ paths.
 

### 2015-05-07 draft.tex
slight changes in lp formulation section
started algorithm analysis

@@
 \usepackage{graphicx}
+\usepackage{clrscode4e}
 
@@
 
-We can formulate a cut-based integer linear program for SSC. We will have a variable
+We can formulate a cut-based integer linear program for SSC. For each edge, we have the variable $x_e$ defined as
 \begin{align}
  x_e &= \left\{ \begin{array}{cc} 1 & e \in H \\
-                                  0 & \text{ otherwise } \end{array} \right.
+                                  0 & \text{ otherwise. } \end{array} \right.
 \end{align}
-So $H$ will be the subgraph consisting of the edges $e$ where $x_e = 1$. \\ \\
+$H$ will be the subgraph consisting of edges $e$ where $x_e = 1$. \\ \\
 SSC-LP:
@@
 
+Now we will combine the ideas of the linear program to approximate the survival set connectivity.
+We copy the algorithm as it is written in the paper below, although we will separate the algorithm into portions and explain each portion in detail.
+\begin{codebox}
+\li Set $H \leftarrow \emptyset$
+\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
+\li Let $x' \leftarrow x*\frac{4}{k}$. 
+\li Prepare $\mathcal{D}$ be the distribution of Racke tree embeddings for $G$ with $x'$.
+\li \For $\tau$ rounds \Do
+\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
+\li \For $q = 0, ..., 2\log n$ \Do
+\li \For $v \in V_t$ \Do
+\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $v$
+\li \If $v$ is $q$-marked \Then
+\li Set $y^{v, q}\leftarrow 2^{q+1}y$ and $E^{v,q} \leftarrow \emptyset$.
+\li \For $\tau'$ iterations, \Do
+\li $E^{v,q} \leftarrow E^{v,q} \cup$ RoundGKR$(T_v, v, y^{v,q})$ \End
+\li $H \leftarrow H \cup \text{map}(E^{v,q})$ \End \End \End \End
+\li return $H$
+\end{codebox}
+
+In order to understand the ideas of the algorithm, it is important to understand the ideas of the analysis. We summarize the ideas of the analysis here:
+\begin{enumerate}
+\item Set a particular set of edges $F$ of size at most $\Omega(\dfrac{k}{\log n})$. 
+\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. 
+\item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$.
+This flow must go up the tree to some common ancestor $v$ and then back down.
+\item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
+\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
+\end{enumerate}
+
 \subsection{Analysis}
+
+It is straight forward to show that the cost is not too bad.
+
+\begin{lemma}
+$\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
+\end{lemma}
+This shows that if the algorithm has $\Omega(\frac{k}{\log n})$ edge-disjoint paths between each $(S_i, T_i)$ pair, then it is a polylogarithmic approximation.
+
+\begin{proof}
+The proof follows the common strategy: we bound the probability that a given edge is included.
+If the probabability that a given edge is included is bounded by $O(\log^4n(\frac{\log h}{k} + 1))x_e$, then by linearity of expectation, we would show the claim.
+
+Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$.
+By line $12$ of the algorithm, for an edge $e \in H$, there needs to be some $e' \in E_t$ such that $e \in \text{map}(e')$ and $e' \in E^{v,q}$ for some $v \in V_t$ and $q$.
+In addition, $v$ needed to have been $q$-marked.
+
+For each $q$ and $v$, $v$ is $q$-marked with probability at most $\frac{4}{2^{-q}}$.
+In any of the $\tau'$ iterations of the RoundGKR algorithm where $v$ was $q$-marked, an edge is selected with probability $2^{q+1}y_e$.
+
+Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e$ is included is at most 
+\begin{align}
+height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_e \tau' &= height(T) \tau' y_2 \sum_q 2 \\
+&= O(\log^3 n) y_e 
+\end{align}
+This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values.
+
+So we have shown that the probability that a given edge is included in a particular sampling of a Racke tree is $O(\log^3 n) y_e$.
+
+\end{proof}
 

### 2015-05-07 draft.tex
adding files and did cost proof

@@
 In any of the $\tau'$ iterations of the RoundGKR algorithm where $v$ was $q$-marked, an edge is selected with probability $2^{q+1}y_e$.
+Figure~\ref{fig:roundgkronnode} shows a possible execution when there is some value of flow found when node $v$ has been $q$-marked.
 
-Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e$ is included is at most 
+Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
 \begin{align}
-height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_e \tau' &= height(T) \tau' y_2 \sum_q 2 \\
-&= O(\log^3 n) y_e 
+height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
+&= O(\log^3 n) y_{e'} 
 \end{align}
@@
 
-So we have shown that the probability that a given edge is included in a particular sampling of a Racke tree is $O(\log^3 n) y_e$.
+So we have shown that the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.
 
+So now in order to include some edge $e$ of the graph, we must include some edge $e' \in \text{map}^{-1}(e)$.
+So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$, and $Y_{e'}$ be the indicator random variable which says that edge $e'$ in the tree is included in some RoundGKR execution.
+Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
+\begin{align}
+X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
+\end{align}
+Because if $e$ is included in the graph, it must have come from some edge in the tree. 
+\begin{align}
+ \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
+        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
+        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
+        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
+        & = \dfrac{O(\log^4 n)\tau}{k} x_e
+\end{align}
+So now, bounding the optimum, we get
+\begin{align}
+\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
+                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
+\end{align}
+So when $\tau = O(\log h + k)$, we get our desired approximation.
 \end{proof}
+
+\begin{figure}
+\label{fig:roundgkronnode}
+\centering
+\includegraphics[width=\linewidth]{RoundGKRonNode.pdf}
+\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
+\end{figure}
 

### 2015-05-08 draft.tex
started correctness proof

@@
 
-In order to understand the ideas of the algorithm, it is important to understand the ideas of the analysis. We summarize the ideas of the analysis here:
-\begin{enumerate}
-\item Set a particular set of edges $F$ of size at most $\Omega(\dfrac{k}{\log n})$. 
-\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. 
-\item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$.
-This flow must go up the tree to some common ancestor $v$ and then back down.
-\item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
-\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
-\end{enumerate}
-
 \subsection{Analysis}
@@
 
+Having established that the expected cost is only polylogarithmic away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.
+
+\begin{definition}
+For some set of edges $F \subset E$, the sampled tree embedding, $(T, y, \text{map})$ is bad if $F_T = \text{map}^{-1}(F)$ 
+\[ \sum_{e' \in F_T} y_{e'} \geq \frac{1}{2} \]
+And good otherwise.
+\end{definition}
+
+Intuitively, bad sets correspond to sets which are necessary in the graph. We want graphs to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity.
+
+\begin{lemma}
+\label{lem:notbad}
+Fix some $F$, or size at most $\dfrac{k}{16 \alpha}$. Then the probability that a sampled tree embedding $(T, y, \text{map})$ from $\mathcal{D}$ is bad is at most $\frac{1}{2}$. 
+\end{lemma}
+
+\begin{proof}
+Suppose we have a bad embedding for the set $F$. Then 
+\begin{align}
+\sum_{e \in F} load(e)&= \sum_{e \in F} \sum_{e' \in \text{map}^{-1}(e)} y_{e'} \\
+                    &\geq \sum_{e' \in F_T} y_{e'} \\
+                    &\geq \frac{1}{2}
+\end{align}
+Where the first inequality we get from taking the sum over the union versus the disjoint union, and the second inequality from the assumption that the tree embedding is bad.
+
+Therefore, a bad tree means that the load of the set of $F$ is more than $\frac{1}{2}$. Therefore,
+\begin{align}
+Pr[\text{pick a bad tree for $F$}] &\leq Pr[ \sum_{e\in F} load(e) \geq \frac{1}{2}]
+\end{align}
+From Lemma~\ref{lem:rload}, we know that
+\begin{align}
+\textbf{E}[ \sum_{e \in F} load(e) ] &\leq \sum_{e \in F} \textbf{E}[rload(e)]x_{e'} \\
+                                   & \leq \sum_{e\in F} \alpha \frac{4}{k} x_{e} \\
+                                   & \leq \dfrac{4\alpha}{k} |F| \\
+                                   &\leq \frac{1}{4}
+\end{align}
+Since we limited the size of $F$. Now invoking Markov's inequality, we know that the probability of bad event is at most $\frac{1}{2}$. 
+\end{proof}
+
+\begin{lemma}
+With probability at least $\frac{3}{4}$, all set pairs are at least $\frac{k}{16\alpha} + 1$ edge connected in $H$. 
+\end{lemma}
+
+\textbf{Proof Idea}:
+\begin{enumerate}
+\item Set a particular set of edges $F$ of size at most $\Omega(\dfrac{k}{\log n})$. 
+\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. (This is Lemma~\ref{lem:notbad}). 
+\item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$.
+This flow must go up the tree to some common ancestor $v$ and then back down.
+\item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
+\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
+\end{enumerate}
+
+\begin{proof}
+We fix an $F$ of size at most $\frac{k}{16\alpha}$ and an $i$ and show that $(S_i, T_i)$ are connected with an edge outside of $F$.
+I will show this happens with a probability at least $\beta$.
+So the probability of failure is $(1-\beta)$.
+If we repeat this $\tau = \frac{1}{\beta}\ln(4hn^{\frac{k}{16\alpha}})$ times, then our failure probability goes down to $\dfrac{1}{4hn^{\frac{k}{16\alpha}}}$.
+So now we take the union bound over all of $F$ and over all $i$, so we get probability of failure at most $\frac{1}{4}$.
+\end{proof}
+
 \section{Conclusion}

### 2015-05-08 draft.tex
really bad proof

@@
 So now we take the union bound over all of $F$ and over all $i$, so we get probability of failure at most $\frac{1}{4}$.
+
+It remains to show that the probability that we find a path from $S_i$ to $T_i$ without using the edges from $F$ is at least $\beta$. We do this in the following lemma.
+\end{proof}
+
+\begin{lemma}
+Fix some $F$ and some $i$, where $|F| < \dfrac{16k}{\alpha}$. The probability that at round $t$ we find a path from $S_i$ to $T_i$ without using edges from $F$ is at least some constant $\beta > 0$. 
+\end{lemma}
+
+\begin{proof}
+We condition on the probability that $F$ is good at round $t$, which by Lemma~\ref{lem:notbad} is at least $\frac{1}{2}$.
+Now we can set the $y$ terms of $F_T = \text{map}^{-1}(F)$ to zero, in order to avoid picking an edge in $F$.
+
+Since we have a good embedding with respect to $F$.
+The assumption was that $G$ can support a flow of at least $k$ in the original graph (by the solution to the fractional linear program).
+Recall that we reweighed the values $x$ by $\frac{4}{k}$, so we can support a flow of at least $4$ in the original graph with $x'$.
+So by Lemma~\ref{lem:mapflows}, $T$ supports a flow from $S_i' = \text{map}^{-1}(S_i)$ to $T_i' = \text{map}^{-1}(T_i)$ of value at least $4$.
+
+Now for some reason, when we remove a total capacity of $\frac{1}{2}$, we are left with a flow of $2 - \frac{1}{2} = \frac{3}{2}$.
+In particular, we can support a unit flow from $S_i'$ to $T_i'$.
+That unit flow can be decomposed into paths $P_1, ..., P_z$, disregarding paths with very small amount of flow $(\leq \frac{1}{2n^2})$.
+So each path goes up from a leaf, turns at some $v$, and then goes down to another leaf.
+Let $\phi_v$ be the flow turning at $v$.
+
+Since we support a flow of at least $\frac{3}{2}$ and we removed paths with at most $\frac{1}{2n^2}$ flow, we are left with
+\[ \phi_v \geq \frac{3}{2} - \dfrac{1}{2n^2}|E_T] \geq 1 \]
+Now $\phi_v$ falls between some $(2^{-q_v-1}, 2^{-q_v}]$ for some $q_v \in \{0, ..., 2\log_2 n\}$.
+Now the probability that none of the $v \in V_T$ is $q$-marked exactly at $q_v$ when we have a good embedding is at most $e^{-3/4}$ which follows by a Chernoff bound.
+So conditioning on this happening, the path gets multiplied by $2^{q_v+1}$ and so it supports a flow of $1$.
+Now Lemma~\ref{lem:findpath} says the path will be included with probability at least $1 - (1 - \Omega(1/\log n))^{\tau'}$.
+If we let $\tau' = O(\log n)$, then we get any constant probability $\epsilon$.
+Since we need to find both paths from the root to both leaves, we get a failure probability of $2\epsilon$.
+
+So the probability that we find a path outside of $F$ is at least one minus the union bound over failure probabilities. This is $1 - \frac{1}{2} - e^{-3/4} - 2\epsilon > 0$. 
 \end{proof}

### 2015-05-08 draft.tex
made changes to rackes tree section

@@
 
-\subsection{Racke Tree Black Box}
+\subsection{R\"{a}cke Tree Black Box}
 
-We will use a particular type of tree embedding which will allow us to paths in the tree to paths in the graph.
+We will use a particular type of tree embedding which will allow us to map paths in the tree to paths in the graph.
 
 \begin{definition}
-For a given graph $G = (V, E)$, a Racke Tree is a tree embedding of $G$, $(T, y, \text{map})$ such that:
+For a given graph $G = (V, E)$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ of $T$, and $\mathrm{map}$ is a function $V_T \cup E_T \to V \cup 2^E$ satisfying the following properties:
 \begin{enumerate}
-\item $\text{map}$ restricted to the leafs of $T$ is a bijection with the vertices of $G$.
-\item For each edge $e \in E_t$ joining $u$ and $v$, $\text{map}(e)$ is a path joining nodes $\text{map}(u)$ and $\text{map}(v)$.
-\item For some edge $e \in E_t$, $y_e$ (the cost of the edge) is a special quantity.
+\item $\mathrm{map}$ restricted to the leaves of $T$ is a bijection with the vertices of $G$.
+In other words, each leaf of the tree $T$ is in one-to-one correspondence with a vertex of the original graph, $G$.
+\item For each edge $e \in E_T$ joining $u$ and $v$, $\text{map}(e)$ is a path joining nodes $\text{map}(u)$ and $\mathrm{map}(v)$.
+\item For some edge $e \in E_T$, $y_e$ (the cost of the edge) is a special quantity.
 Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$.

### 2015-05-08 draft.tex
made further changes to rackes tree section

@@
 
-\subsection{R\"{a}cke Tree Black Box}
+\subsection{R\"{a}cke's Trees}
 
@@
 \begin{enumerate}
-\item $\mathrm{map}$ restricted to the leaves of $T$ is a bijection with the vertices of $G$.
+\item For each node $v \in V_T$, $\mathrm{map}(v) \in V$. Thus, the $\mathrm{map}$ function maps nodes in the tree $T$ to nodes in the original graph, $G$.
+\item Furthermore, $\mathrm{map}$ restricted to the leaves of $T$ is a bijection with the vertices of $G$.
 In other words, each leaf of the tree $T$ is in one-to-one correspondence with a vertex of the original graph, $G$.
-\item For each edge $e \in E_T$ joining $u$ and $v$, $\text{map}(e)$ is a path joining nodes $\text{map}(u)$ and $\mathrm{map}(v)$.
-\item For some edge $e \in E_T$, $y_e$ (the cost of the edge) is a special quantity.
+\item For each edge $e = (u,v) \in E_T$, $\mathrm{map}(e)$ is a set of edges that form a path between $\mathrm{map}(u)$ and $\mathrm{map}(v)$.
+Note that $\mathrm{map}(u)$ and $\mathrm{map}(v)$ are vertices in $G$, so $\mathrm{map}(e)$ specifies a set of edges in $G$.
+%\item For some edge $e \in E_T$, $y_e$ (the cost of the edge) is a special quantity.
 Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$.
@@
 \end{definition}
+
+To summarize, the $\mathrm{map}$ function sends vertices in $V_T$ to vertices in $V$, and sends edges in $T$ to paths in $G$.
+With these definitions, we can consider the inverse function $\mathrm{map}^{-1}$.
+Note that multiple vertices in $T$ could map to the same vertex in $V$, so we must specify that for $v \in G$, the value of $\mathrm{map}^{-1}(v)$ is the unique \emph{leaf} vertex in $V_T$ that maps to $v$.
+We will also consider $\mathrm{map}^{-1}$ applied to sets of vertices $W \subseteq V$, and define it in the obvious way: $\mathrm{map}^{-1}(W) = \bigcup_{v \in W} \mathrm{map}^{-1}(v)$.
 

### 2015-05-09 draft.tex
made more changes to rackes trees

@@
 Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
-\begin{align}
-y_e &= \sum_{e' \in \delta(S)} x_e
-\end{align}
+%\begin{align}
+%y_e &= \sum_{e' \in \delta(S)} x_e
+%\end{align}
 \end{enumerate}
@@
 
-To summarize, the $\mathrm{map}$ function sends vertices in $V_T$ to vertices in $V$, and sends edges in $T$ to paths in $G$.
-With these definitions, we can consider the inverse function $\mathrm{map}^{-1}$.
-Note that multiple vertices in $T$ could map to the same vertex in $V$, so we must specify that for $v \in G$, the value of $\mathrm{map}^{-1}(v)$ is the unique \emph{leaf} vertex in $V_T$ that maps to $v$.
-We will also consider $\mathrm{map}^{-1}$ applied to sets of vertices $W \subseteq V$, and define it in the obvious way: $\mathrm{map}^{-1}(W) = \bigcup_{v \in W} \mathrm{map}^{-1}(v)$.
+With this setup, we can try to define the inverse function, $\mathrm{map}^{-1}$.
+If we try to compute $\mathrm{map}^{-1}(v)$ for some $v \in V$, we note that multiple vertices in $T$ could map to $v$.
+Thus, we specify that $\mathrm{map}^{-1}(v)$ be the unique \emph{leaf} vertex in $V_T$ that maps to $v$.
+We will also consider $\mathrm{map}^{-1}$ applied to sets of vertices $W \subseteq V$, and we define it in the obvious way: $\mathrm{map}^{-1}(W) = \bigcup_{v \in W} \mathrm{map}^{-1}(v)$.
+
+For edges $e = (u,v) \in E$, we define $\mathrm{map}^{-1}(e) = \{ f \in E_T | e \in \mathrm{map}(f)\}$.
+This is simply the set of all edges $f$ in the tree $T$ that get mapped to a set of edges $\mathrm{map}(f)$ that contain $e$.
+Again, this defintiion can be extended to sets of edges $F \subseteq E$, so that $\mathrm{map}^{-1}(F) = \bigcup_{e \in F} \mathrm{map}^{-1}(e)$.
 
@@
 \end{figure}
-
-Having made these definition, we can refer to the inverse $\text{map}^{-1}$ in the obvious manner.
-$\text{map}^{-1}$ on a vertex will map to the corresponding leaf, and $\text{map}^{-1}$ on an edge in the graph will map to all edges in the tree whose paths contain that edge.
 

### 2015-05-09 draft.tex
further changes to rackes trees

@@
 Again, this defintiion can be extended to sets of edges $F \subseteq E$, so that $\mathrm{map}^{-1}(F) = \bigcup_{e \in F} \mathrm{map}^{-1}(e)$.
+
+Finally, we for an edge $e \in E_T$, we define $y_e$ as follows.
+The removal of $e$ from $T$ separates the tree into two connected components.
+Let $S$ be the set of vertices of $G$ mapped to by the leaves of one of the connected component, and so $V \setminus S$ is the set of vertices of $G$ mapped to by the leaves of the other connected component.
+Define $\delta(S)$ to be the set of edges in $E$ that cross from $S$ to $V \setminus S$.
+Then we set $y_e = \sum_{e' \in \delta(S)} x_e$.
 

### 2015-05-09 draft.tex
small changes to rackes trees

@@
 \begin{definition}
-For a given graph $G = (V, E)$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ of $T$, and $\mathrm{map}$ is a function $V_T \cup E_T \to V \cup 2^E$ satisfying the following properties:
+For a given graph $G = (V, E)$ with edge capacities $x_e \geq 0$, $e \in E$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ of $T$, and $\mathrm{map}$ is a function $V_T \cup E_T \to V \cup 2^E$ satisfying the following properties:
 \begin{enumerate}
@@
 
-With this setup, we can try to define the inverse function, $\mathrm{map}^{-1}$.
+With this setup, we can define the inverse function, $\mathrm{map}^{-1}$.
 If we try to compute $\mathrm{map}^{-1}(v)$ for some $v \in V$, we note that multiple vertices in $T$ could map to $v$.
@@
 
-Finally, we for an edge $e \in E_T$, we define $y_e$ as follows.
+Finally, for an edge $e \in E_T$, we define $y_e$ as follows.
 The removal of $e$ from $T$ separates the tree into two connected components.
@@
 Define $\delta(S)$ to be the set of edges in $E$ that cross from $S$ to $V \setminus S$.
-Then we set $y_e = \sum_{e' \in \delta(S)} x_e$.
+Then we set $y_e = \sum_{e' \in \delta(S)} x_{e'}$, the total edge capacity crossing the cut.
 
@@
 \includegraphics[width=0.5\linewidth]{Rackecut.pdf}
-\caption{Racke tree cut induced by an edge in the tree.}
+\caption{R\"{a}cke's tree cut induced by an edge in the tree.}
 \end{figure}
@@
 \begin{definition}
-Given a Racke tree, the load on an edge of the graph $e \in E$ is
+Given a R\"{a}cke tree, the load on an edge of the graph $e \in E$ is
 \begin{align}
-load(e) &= \sum_{f \in \text{map}^{-1}(e)} y_f
+load(e) &= \sum_{f \in \text{map}^{-1}(e)} y_f,
 \end{align}
-The relative load, $rload(e) = \dfrac{load(e)}{x_e}$. 
+and the relative load is defined as 
+\begin{align}
+rload(e) = \dfrac{load(e)}{x_e}.
+\end{align}
 \end{definition}

### 2015-05-09 draft.tex
finished making changes to rackes tree section

@@
 The removal of $e$ from $T$ separates the tree into two connected components.
-Let $S$ be the set of vertices of $G$ mapped to by the leaves of one of the connected component, and so $V \setminus S$ is the set of vertices of $G$ mapped to by the leaves of the other connected component.
+Let $S$ be the set of vertices of $G$ mapped to by the leaves of one of the connected components, and so $V \setminus S$ is the set of vertices of $G$ mapped to by the leaves of the other connected component.
 Define $\delta(S)$ to be the set of edges in $E$ that cross from $S$ to $V \setminus S$.
@@
 
-Figure~\ref{fig:racketree} gives an example of a Racke tree with the mapping.
+The usefulness of R\"{a}cke's trees becomes apparent when we consider multi-commodity flows.
+Recall that the multi-commodity flow problem specifies $k$ different commodities, where each commodity $i$ must be routed from source $s_i$ to sink $t_i$, subject to constraints on the capacity of each edge.
+The resulting flow can be represented as a set of functions $\{ f_i \}$, where $f_i(e)$ is the nonnegative real number amount of commodity $i$ flowing on edge $e$.
+
+There is a natural way to map multi-commodity flows between $G$ and $T$.
+In particular, suppose we have a multi-commodity flow $\{ f_i \}$ on $G$.
+For each $i$, if there are $f_i$ units of flow going from $s_i$ to $t_i$ in $G$, we route $f_i$ units of flow in the $T$ from $\mathrm{map}^{-1}(s_i)$ to $\mathrm{map}^{-1}(t_i)$.
+If we are given a multicommodity flow $\{ f_i^T \}$ in $T$, then if we have $f_i^T(e)$ units of flow on edge $e$ in $T$, then we route $f_i^T(e)$ units of flow through the path $\mathrm{map}(e)$ in $G$ (recall that edges in $T$ map to paths in $G$).
+
+Figure~\ref{fig:racketree} gives an example of the flow correspondnece between a graph and it's associated R\"{a}cke's tree.
 Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices.
 This gives us a simple way to map flows from Racke trees to the graph and vice-versa.
-
-In particular, if we have a multicommodity flow $\{ f_i \}$ on the graph, then we can easily map into a multicommodity flow on the Racke tree.
-If there is a flow $f_i$ from $s_i$ to $t_i$, then we find leaves $s_i^{T}=\text{map}^{-1}(s_i)$ and $t_i^T\text{map}^{-1}(t_i)$ and route $f_i$ units of flow through the unique path from $s_i$ to $t_i$.
-
-For obtaining a flow on the graph given one on the Racke tree, if $f_i^T(e)$ is the flow of commodity $i$ on the tree on $e \in E_t$, then we route $f_i^T(e)$ units of flow down the path given by $\text{map}(e)$.
 

### 2015-05-09 draft.tex
made lots of small changes to roundgkr section

@@
 
-The next tool we will need are tree embeddings.
+%The next tool we will need are tree embeddings.
 We have seen metric embeddings in class.
 Basically, we had a desired type of object $O$ (in the case of cuts, we had a metric space corresponding to a cut) what we did was come up with a metric space $(X, d)$ and a map $f: (X, d) \rightarrow O$ such that the map satisfied certain properties on the distances.
-
-Here we will have a similar goal.
+%
+%Here we will have a similar goal.
 We want to understand minimum cost weighted graphs, but since analyzing them is hard, we instead study minimum cost weighted trees, and then we map the trees back to the graphs.
-
-\begin{definition}
-A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}^{\geq 0}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
-\begin{align}
-\text{map}(V_t) &\subset V \\
-\text{map}(E_t) &\subset E
-\end{align}
-In other words, vertices map to vertices and edges map to edges. We will usually refer to an embedding as $(T, y, \text{map})$. 
-\end{definition}
+%
+%\begin{definition}
+%A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}^{\geq 0}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
+%\begin{align}
+%\text{map}(V_t) &\subset V \\
+%\text{map}(E_t) &\subset E
+%\end{align}
+%In other words, vertices map to vertices and edges map to edges. We will usually refer to an embedding as $(T, y, \text{map})$. 
+%\end{definition}
 
@@
 
-The RoundGKR algorithm is an algorithm to rounding algorithm used for the Group Steiner Tree problem. We first describe the problem and give the algorithm. \\
+The RoundGKR algorithm is a rounding procedure used to solve the Group Steiner Tree (GST) problem. The problem it stated as follows. \\
 
@@
 \begin{quote}
-\textbf{Input}: A rooted tree $T = (V_t, E_t)$ at $r$ with costs $c: E_t \rightarrow \mathbb{R}^{\geq 0}$ as well as subsets of vertices $\{ T_i \}$. \\
-\textbf{Output}: A minimum cost subtree $H \subset T$ with a path from $r$ to $t_i$ for some $t \in T_i$ for all $i$.
+\textbf{Input}: A tree $T = (V_T, E_T)$ rooted at $r$ where each edge has a nonnegative real value cost $c(e)$, along with a set $\{T_i\}$ where each $T_i \subseteq V_T$.\\
+\textbf{Output}: The minimum cost subtree $H \subseteq T$ with a path from $r$ to $t_i$ for some $t \in T_i$ for all $i$.
 \end{quote}
 
-A similar linear program produces a fractional solution, and the algorith RoundGKR is a way of rounding the solution back.
-The optimum to the linear program will be a set of values for each edge $y_e \in [0, 1]$.
-Since we are in a tree setting and we are looking for paths from the root, we can assume that $y_{p(e)} \geq y_e$ (parent edges are always greater).
+The following integer linear program solves the problem exactly:\\
+GST-ILP:
+\begin{align}
+\min & \sum c(e) y_e  \\
+\text{ s.t } & \sum_{e \in \delta(S)} y_e \geq 1, \text{ where } S_i \subset S, T_i \subset V - S, \delta(S) \text{ is the edges of the $S$ cut }
+\end{align}
 
-The RoundGKR is simple, it starts at the root and makes its way down the tree as its being built.
-It includes the edge $e$ in the subtree with probability $\frac{y_e}{y_{p(e)}}$.
-A simple inductive argment shows that an edge $e$ is chosen with probability $y_e$.
-This is because $Pr[\text{include $e$}] = Pr[\text{include $e$ $|$ include $p(e)$}]*Pr[\text{include $p(e)$}] = y_e$ (if we don't include $p(e)$, then we don't include $e$.
+If we relax the integer linear program to a linear program and solve it, we can use RoundGKR to round the resulting fractional solution to an integer solution.
+The optimum to the linear program will assign fractional values in $[0,1]$ to each $y_e$.
+For any $e$, let $p(e)$ denote its parent edge (if it exists).
+We claim that since our problem is to find a subtree that includes the root $r$, edges that are closer to the root are at least as likely to be included in the subtree than edges farther from the root.
+Since the value of $y_e$ will be used as the probability that edge $e$ is included in $H$, we will assume that $y_{p(e)} \geq y_e$.
+
+The RoundGKR procedure simply starts at the root $r$ and builds the subtree $H$ by working its way down the original tree, $T$.
+It decides whether or not to include edge $e$ only once it has included edge $p(e)$ (if ever).
+At this step, it includes $e$ with probability $\frac{y_e}{y_{p(e)}}$.
+A simple inductive argment shows that an edge $e$ is chosen with probability $y_e$ (proof sketch: assume by induction that we know $Pr[\text{include $p(e)$}] = y_{p(e)}$.
+Then $Pr[\text{include $e$}] = Pr[\text{include $e$ $|$ include $p(e)$}]*Pr[\text{include $p(e)$}] = \frac{y_e}{y_{p(e)}}y_{p(e)} = y_e$.)
 

### 2015-05-10 draft.tex
small changes to roundgkr section
rewrote the intro, commented old stuff out

@@
 
-Note that this problem generalizes the common connectivity problems.
-The question of whether there are $k$ connections between $s$ and $t$ sets only one pair $(S_1, T_1)$ where $S_1 = \{ s \}$ and $T_i = \{ t \}$.
+Unfortunately, solving exact Survivable Set Connectivity is $\mathsf{NP}$-hard [CITATION].
+Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem.
+Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths.
+With this relaxation, it is possible to find a subgraph with cost $O(polylog(n)$ times the optimum.
 
-[ GIVE MORE EXAMPLES HERE ]
-
-As with many of these kinds of problems, SSC is $\mathsf{NP}$-hard.
+The paper is organized as follows.
+We first present a natural integer linear programming formulation of the problem.
+Then, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm.
+We also show a general rounding scheme, called RoundGKR, which our algorithm uses as a black box.
+Finally, we combine all these concepts together to present and analyze an approximation algorithm for SSC.
+%
+%[ GIVE MORE EXAMPLES HERE ]
+%
+%As with many of these kinds of problems, SSC is $\mathsf{NP}$-hard.
 The common route taken in 6.856 has been to find polynomial time algorithms for approximations; however, in the case with SSC, it is $\mathsf{NP}$-hard to achieve a polylogarithmic approximation.
-
-Another possible approach is therefore to relax the question.
+%
+%Another possible approach is therefore to relax the question.
 Instead of requiring at least $k$ edge-disjoint paths, we will allow some sets to have less than $k$ paths, but not too much less.
 We will present an approximation algorithm which outputs a subgraph of cost $O(polylog(n))$ times the optimum such that for each $(S_i, T_i)$ pairs, there are at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths between $S_i$ and $T_i$.
-
-The approximation algorithm will follow the usual approach to approximation algorithms of this kind.
+%
+%The approximation algorithm will follow the usual approach to approximation algorithms of this kind.
 We will first write the problem as an integer linear program, we solve the linear programming relaxation, and then we round the solution.
-
-The analysis will be slightly different from the analysis shown in class.
+%
+%The analysis will be slightly different from the analysis shown in class.
 Usually, our randomized algorithm will return a feasible solution to the problem, and our analysis work is mostly to bound the cost.
@@
 
-The important property of the algorithm can be summarized in the following lemma, whose proof we refer to [CITE].
+The important property of the algorithm can be summarized in the following lemma, whose proof can be found in [CITE].
 

### 2015-05-10 draft.tex
fixed a typo
changed margins,rewrote LP formulation sections, fixed typos

@@
 \usepackage{clrscode4e}
+\usepackage{geometry}
+ \geometry{
+ a4paper,
+ total={210mm,297mm},
+ left=20mm,
+ right=20mm,
+ top=20mm,
+ bottom=20mm,
+ }
 
@@
 Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths.
-With this relaxation, it is possible to find a subgraph with cost $O(polylog(n)$ times the optimum.
+With this relaxation, it is possible to find a subgraph with cost $O(polylog(n))$ times the optimum.
 
@@
 
-\section{Linear Programming Formulation}
+\section{An Integer Linear Program}
 
-We can formulate a cut-based integer linear program for SSC. For each edge, we have the variable $x_e$ defined as
+In this section, we give an integer linear program that exactly solves SSC.
+Recall that the goal is to output a subgraph $H$ of $G$ such that each $(S_i,T_i)$ pair has at least $k$ edge disjoint paths.
+Naturally, we create an indicator variable $x_e$ for each edge based on whether or not it is included in $H$.
 \begin{align}
@@
 \end{align}
-$H$ will be the subgraph consisting of edges $e$ where $x_e = 1$. \\ \\
+Thus, our output $H$ will be the subgraph consisting of edges $e$ where $x_e = 1$. \\ \\
+
+We claim that the following ILP captures SSC exactly. 
 SSC-LP:
@@
 \min & \sum c(x) x_e  \\
-\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{ where } S_i \subset S, T_i \subset V - S, \delta(S) \text{ is the edges of the $S$ cut }
+\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{for each }S\text{ where } S_i \subset S,T_i \subset V - S, \\ & \hspace{1in}\delta(S) \text{ is the edges of the $S$ cut } \\
+& x_e \in [0,1] \text{ for all }e \in E
 \end{align}
-This cut-based integer linear program finds exactly $H$.
+
+The objective function $\sum c(x) x_e$ simply minimizes the cost of all edges included in $H$.
+The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut.
+This property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
+We omit the proof of this statement, but it can be found in [CITATION].
+
+%
+%
+% 
+%This cut-based integer linear program finds exactly $H$.
 To see why the constraints ensure that each $(S_i, T_i)$ pair has at least $k$ edge disjoint paths, we can look at the cuts corresponding to $S_i$ and $T_i$.
@@
 
-There is one caveat that has not been addressed.
-We have exponentially many constraints!
-Since there can be exponentially many set $S$ with $S_i \subset S$ and $T_i \subset V - S$.
-We solve this with a similar idea to semi-definite programming, by giving a separation oracle which runs in polynomial time.
+Of course, since this is an integer linear program, we must relax it to fractional solutions in order to solve it.
+Thus, we relax the constraint of $x_e \in [0,1]$ to $0 \leq x_e \leq 1$.
+However, there is still a slight issue; there can be exponentially many constraints.
+This is because there are exponentially many choices of $S$ for each $(S_i,T_i)$ pair.
+To get around this issue, we note that the ellipsoid algorithm can handle linear programs with arbitrarily many constraints, as long as it is given a separation oracle.
+Luckily, we can give such an oracle.
 
-The separation oracle will just compute the minimum $S_i, T_i$ cut in the graph.
-What we can do is contract $S_i$ and $T_i$ to single edges, and then compute the min-cut in the remaining graph.
+The separation oracle just computes the minimum $S_i, T_i$ cut in the graph.
+What we can do is contract $S_i$ and $T_i$ to single vertices, and then compute the min-cut in the remaining graph.
 If there is a min-cut of size less than $k$, then that cut will correspond to a violating contraint.
 If the min-cut has size at least $k$, then all cuts have size at least $k$, so we have satisfied the constraints.
-
-The linear programming relaxation to the above program will be the first step of the algorithm.
-The remaining work will be rounding the fractional solution to an integral solution and satisfy the constraints.
 
@@
 
-Figure~\ref{fig:racketree} gives an example of the flow correspondnece between a graph and it's associated R\"{a}cke's tree.
+Figure~\ref{fig:racketree} gives an example of the flow correspondence between a graph and it's associated R\"{a}cke's tree.
 Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices.

### 2015-05-10 draft.tex
adding references and shrinking images

@@
 
-Unfortunately, solving exact Survivable Set Connectivity is $\mathsf{NP}$-hard [CITATION].
-Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem.
+Unfortunately, solving exact Survivable Set Connectivity is $\mathsf{NP}$-hard \cite{ssc}.
+Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem given in \cite{ssc}.
 Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths.
@@
 This property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
-We omit the proof of this statement, but it can be found in [CITATION].
-
 %
@@
 
-We will use a particular type of tree embedding which will allow us to map paths in the tree to paths in the graph.
+We will use a particular type of tree embedding given in \cite{racke} which will allow us to map paths in the tree to paths in the graph.
 
@@
 \centering
-\includegraphics[width=\linewidth]{Rackeembeddinggraph.pdf}
+\includegraphics[width=0.8\linewidth]{Rackeembeddinggraph.pdf}
 \caption{Example Racke Tree where red nodes are mapped and edge maps to a path.}
@@
 
-\begin{lemma}
+\begin{lemma}[\cite{racke}]
 \label{lem:mapflows}
@@
 
-\begin{lemma}
+\begin{lemma}[\cite{racke}]
 \label{lem:rload}
@@
 
-\begin{lemma}
+\begin{lemma}[\cite{ssc}]
 \label{thm:height}
@@
 
-The RoundGKR algorithm is a rounding procedure used to solve the Group Steiner Tree (GST) problem. The problem it stated as follows. \\
+The RoundGKR algorithm is a rounding procedure used to solve the Group Steiner Tree (GST) problem \cite{GKR}. The problem it stated as follows. \\
 
@@
 
-\begin{lemma}
+\begin{lemma}[\cite{GKR}]
 \label{lem:findpath}
@@
 
-\begin{lemma}
+\begin{lemma}[\cite{ssc}]
 $\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
@@
 \centering
-\includegraphics[width=\linewidth]{RoundGKRonNode.pdf}
+\includegraphics[width=0.6\linewidth]{RoundGKRonNode.pdf}
 \caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
@@
 
-\begin{lemma}
+\begin{lemma}[\cite{ssc}]
 \label{lem:notbad}
@@
 
-\begin{lemma}
+\begin{lemma}[\cite{ssc}]
 With probability at least $\frac{3}{4}$, all set pairs are at least $\frac{k}{16\alpha} + 1$ edge connected in $H$. 
@@
 
+\bibliography{references}
+\bibliographystyle{splncs}
+
 \end{document}

### 2015-05-10 draft.tex
added intuitive exaplanation

@@
 
+\subsection{Algorithm Idea}
+
+Here, we provide an intuitive explanation of the algorithm as well as the main motivations for each procedure. Of course, we will revist these ideas in the analysis.
+
+After running the linear program, we rescale $x$ to $x'$ by $\frac{4}{k}$ to ensure we have a flow of at least $4$ in each pair $(S_i, T_i)$.
+This flow of $4$ will correspond to a flow of $4$ on the R\"{a}cke trees.
+
+The RoundGKR algorithm is the main tool used for our rounding scheme.
+RoundGKR guarantees find paths on trees which avoid edges will be found with probability $\Omega(\frac{1}{\log n})$ (this is Lemma~\ref{lem:findpath}) given there is sufficient flow.
+We repeat this $\tau' = O(\log n)$ times to assure a constant probability.
+
+We can only run RoundGKR on trees.
+We introduce R\"{a}cke trees specifically for this purpose.
+We know a flow of $4$ exists between leaves (Lemma~\ref{lem:mapflows}).
+Each flow path will go up the tree to some ancestor $v$ and then back down to a leaf.
+One such path might be found when $v$ gets marked.
+One path will go to $s_i'$ and one to $t_i'$.
+
+Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoinding some edges.
+If a flow path from $s_i'$ to $t_i'$ goes through ancestor $v$ and carries a flow of value $f$, we can apply the lemma if $f \geq 1$.
+We scale the capacities by $2^{q+1}$ in order to search for the flow value.
+We only scale with probabilities $\dfrac{4}{2^q}$ so our costs does not increase by more than $O(\log n)$.
+Figure~\ref{fig:roundgkronnode} shows how a flow path might be found.
+
 \subsection{Analysis}
@@
 
-\section{Conclusion}
-
-\subsection{Open Problems}
-
 \bibliography{references}

### 2015-05-11 draft.tex
started modifying the algorithm part

@@
 
-\section{Tree Embeddings}
-
 %The next tool we will need are tree embeddings.
@@
 
-\subsection{R\"{a}cke's Trees}
+\section{R\"{a}cke's Trees}
 
@@
 
-\subsection{RoundGKR Black Box}
+\section{The RoundGKR Procedure}
 
@@
 
-Now we will combine the ideas of the linear program to approximate the survival set connectivity.
-We copy the algorithm as it is written in the paper below, although we will separate the algorithm into portions and explain each portion in detail.
+Now we will combine the ideas of the linear program to approximate a solution to Survivable Set Connectivity.
+We copy the algorithm as it is written in the paper below, although we will separate the algorithm into parts and explain each part in detail.
 \begin{codebox}
@@
 
-After running the linear program, we rescale $x$ to $x'$ by $\frac{4}{k}$ to ensure we have a flow of at least $4$ in each pair $(S_i, T_i)$.
-This flow of $4$ will correspond to a flow of $4$ on the R\"{a}cke trees.
+After running the linear program, we rescale $x$ to $x'$ by a $\frac{4}{k}$ factor, which ensures that we have a flow of at least $4$ in each $(S_i, T_i)$.
+This flow of $4$ will correspond to a flow of $4$ in the R\"{a}cke's trees.
 
 The RoundGKR algorithm is the main tool used for our rounding scheme.
-RoundGKR guarantees find paths on trees which avoid edges will be found with probability $\Omega(\frac{1}{\log n})$ (this is Lemma~\ref{lem:findpath}) given there is sufficient flow.
-We repeat this $\tau' = O(\log n)$ times to assure a constant probability.
+RoundGKR finds paths in trees which avoid specific edges with probability $\Omega(\frac{1}{\log n})$ (this is Lemma~\ref{lem:findpath}) given there is sufficient flow.
+We repeat this $\tau' = O(\log n)$ times to assure a constant probability of finding such paths.
 
-We can only run RoundGKR on trees.
-We introduce R\"{a}cke trees specifically for this purpose.
+However, we can only run RoundGKR on trees, not general graphs.
+We introduce the R\"{a}cke's tree embedding specifically for this purpose.
 We know a flow of $4$ exists between leaves (Lemma~\ref{lem:mapflows}).
@@
 
-Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoinding some edges.
+Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoiding some edges.
 If a flow path from $s_i'$ to $t_i'$ goes through ancestor $v$ and carries a flow of value $f$, we can apply the lemma if $f \geq 1$.
@@
 
-It is straight forward to show that the cost is not too bad.
+First, we argue that the cost of the solution found by this algorithm is within polylogarithmic factors of the optimum.
 

### 2015-05-11 draft.tex
drastically changed the algorithm part

@@
 
-\subsection{Analysis}
+\section{Algorithm Analysis}
 
-First, we argue that the cost of the solution found by this algorithm is within polylogarithmic factors of the optimum.
+\subsection{Overview}
 
-\begin{lemma}[\cite{ssc}]
-$\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
-\end{lemma}
-This shows that if the algorithm has $\Omega(\frac{k}{\log n})$ edge-disjoint paths between each $(S_i, T_i)$ pair, then it is a polylogarithmic approximation.
+We claim that the algorithm finds a solution which has
+\begin{itemize}
+\item (Claim A) at least $\Omega(\frac{k}{\log n})$ edge disjoint paths between each $(S_i, T_i)$ pair
+\item (Claim B) cost within a polylogarithmic factor of the optimum
+\end{itemize}
 
-\begin{proof}
-The proof follows the common strategy: we bound the probability that a given edge is included.
-If the probabability that a given edge is included is bounded by $O(\log^4n(\frac{\log h}{k} + 1))x_e$, then by linearity of expectation, we would show the claim.
+We first prove Claim A, and then using Claim A, we prove Claim B.
 
-Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$.
-By line $12$ of the algorithm, for an edge $e \in H$, there needs to be some $e' \in E_t$ such that $e \in \text{map}(e')$ and $e' \in E^{v,q}$ for some $v \in V_t$ and $q$.
-In addition, $v$ needed to have been $q$-marked.
-
-For each $q$ and $v$, $v$ is $q$-marked with probability at most $\frac{4}{2^{-q}}$.
-In any of the $\tau'$ iterations of the RoundGKR algorithm where $v$ was $q$-marked, an edge is selected with probability $2^{q+1}y_e$.
-Figure~\ref{fig:roundgkronnode} shows a possible execution when there is some value of flow found when node $v$ has been $q$-marked.
-
-Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
-\begin{align}
-height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
-&= O(\log^3 n) y_{e'} 
-\end{align}
-This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values.
-
-So we have shown that the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.
-
-So now in order to include some edge $e$ of the graph, we must include some edge $e' \in \text{map}^{-1}(e)$.
-So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$, and $Y_{e'}$ be the indicator random variable which says that edge $e'$ in the tree is included in some RoundGKR execution.
-Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
-\begin{align}
-X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
-\end{align}
-Because if $e$ is included in the graph, it must have come from some edge in the tree. 
-\begin{align}
- \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
-        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
-        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
-        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
-        & = \dfrac{O(\log^4 n)\tau}{k} x_e
-\end{align}
-So now, bounding the optimum, we get
-\begin{align}
-\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
-                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
-\end{align}
-So when $\tau = O(\log h + k)$, we get our desired approximation.
-\end{proof}
-
-\begin{figure}
-\label{fig:roundgkronnode}
-\centering
-\includegraphics[width=0.6\linewidth]{RoundGKRonNode.pdf}
-\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
-\end{figure}
-
-Having established that the expected cost is only polylogarithmic away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.
+\subsection{Claim A}
 
 \begin{definition}
-For some set of edges $F \subset E$, the sampled tree embedding, $(T, y, \text{map})$ is bad if $F_T = \text{map}^{-1}(F)$ 
+For some set of edges $F \subseteq E$, the sampled tree embedding, $(T, y, \text{map})$ is bad if $F_T = \text{map}^{-1}(F)$ 
 \[ \sum_{e' \in F_T} y_{e'} \geq \frac{1}{2} \]
@@
 \label{lem:notbad}
-Fix some $F$, or size at most $\dfrac{k}{16 \alpha}$. Then the probability that a sampled tree embedding $(T, y, \text{map})$ from $\mathcal{D}$ is bad is at most $\frac{1}{2}$. 
+Fix some $F$ of size at most $\dfrac{k}{16 \alpha}$. Then the probability that a sampled tree embedding $(T, y, \text{map})$ from $\mathcal{D}$ is bad is at most $\frac{1}{2}$. 
 \end{lemma}
@@
 
+\subsection{Claim B}
+
+\begin{lemma}[\cite{ssc}]
+$\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
+\end{lemma}
+
+\begin{proof}
+We prove this by bounding the probability that a given edge is included in $H$ by $O(\log^4n(\frac{\log h}{k} + 1))x_e$. The claim then follows by linearity of expectation.
+
+Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$.
+For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_t$ and some index $q \in [0,\dots,2\log n]$.
+For this to occur, $v$ must be $q$-marked, an event that occurs with probability $\frac{4}{2^{-q}}$.
+
+For a given edge $e'$, there are at most $height(T)$ ancestors, which means that there are at most $height(T)$ different vertices $v$ that, if $q$-marked, may lead to $e'$ being included.
+For each $v$, we must consider all $O(\log n)$ possible values of $q$.
+For each value of $q$, the probability of being $q$-marked is $\frac{4}{2^{-q}}$.
+Once the vertex is $q$-marked, we have $\tau'$ trials of the RoundGKR algorithm, where in each trial, there is a $2^{q+1}y_{e'}$ chance of edge $e'$ being included (by construction of the algorithm).
+Multiplying these probablities together and applying a union bound over all $\tau'$ trials and over all possible values of $q$, we get an upper bound of
+
+\begin{align}
+height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 = O(\log^3 n) y_{e'} 
+\end{align}
+
+Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
+\begin{align}
+height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
+&= O(\log^3 n) y_{e'} 
+\end{align}
+This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values.
+So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.
+
+So now in order to include some edge $e$ of the graph $G$, we must include some edge $e' \in \text{map}^{-1}(e)$ (recall that this is the set of tree edges which, if selected, result in edge $e$ being included).
+So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$, and $Y_{e'}$ be the indicator random variable which says that edge $e'$ in the tree is included in some RoundGKR execution.
+Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
+\begin{align}
+X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
+\end{align}
+Because if $e$ is included in the graph, it must have come from some edge in the tree. 
+\begin{align}
+ \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
+        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
+        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
+        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
+        & = \dfrac{O(\log^4 n)\tau}{k} x_e
+\end{align}
+So now, bounding the optimum, we get
+\begin{align}
+\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
+                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
+\end{align}
+So when $\tau = O(\log h + k)$, we get our desired approximation.
+\end{proof}
+
+\begin{figure}
+\label{fig:roundgkronnode}
+\centering
+\includegraphics[width=0.6\linewidth]{RoundGKRonNode.pdf}
+\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
+\end{figure}
+
+Having established that the expected cost is only a polylogarithmic factor away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.
+We will need the following definition.
+
 \bibliography{references}

### 2015-05-11 draft.tex
minor changes

@@
 
-Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
-\begin{align}
-height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
-&= O(\log^3 n) y_{e'} 
-\end{align}
-This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values.
 So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.

### 2015-05-11 draft.tex
minor changes again
D
made lots of changes to claim A

@@
 \section{R\"{a}cke's Trees}
+\label{sec:rackestrees}
 
@@
 
+We refer to $\mathcal{D}$ as the distribution over R\"{a}cke trees with the above properties. In \cite{racke}, there is a polynomial time algorithm for sampling from this distribution.
+
 \section{The RoundGKR Procedure}
@@
 \begin{itemize}
-\item (Claim A) at least $\Omega(\frac{k}{\log n})$ edge disjoint paths between each $(S_i, T_i)$ pair
-\item (Claim B) cost within a polylogarithmic factor of the optimum
+\item (Claim A) cost within a polylogarithmic factor of the optimum
+\item (Claim B) at least $\Omega(\frac{k}{\log n})$ edge disjoint paths between each $(S_i, T_i)$ pair
 \end{itemize}
 
-We first prove Claim A, and then using Claim A, we prove Claim B.
+We first prove Claim A assuming that Claim B is true, and then we prove claim B.
 
 \subsection{Claim A}
+
+\begin{lemma}[\cite{ssc}]
+$\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
+\end{lemma}
+
+\begin{proof}
+We prove this by bounding the probability that a given edge is included in $H$ by $O(\log^4n(\frac{\log h}{k} + 1))x_e$. The claim then follows by linearity of expectation.
+
+Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$.
+For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_t$ and some index $q \in [0,\dots,2\log n]$.
+For this to occur, $v$ must be $q$-marked, an event that occurs with probability $\frac{4}{2^{q}}$.
+
+For a given edge $e'$, there are at most $height(T)$ ancestors, which means that there are at most $height(T)$ different vertices $v$ that, if $q$-marked, may lead to $e'$ being included.
+For each $v$, we must consider all $O(\log n)$ possible values of $q$.
+For each value of $q$, the probability of being $q$-marked is $\frac{4}{2^{q}}$.
+Once the vertex is $q$-marked, we have $\tau'$ trials of the RoundGKR algorithm, where in each trial, there is a $2^{q+1}y_{e'}$ chance of edge $e'$ being included (by construction of the algorithm).
+Multiplying these probablities together and applying a union bound over all $\tau'$ trials and over all possible values of $q$, we get an upper bound of
+
+\begin{align}
+height(T) \sum_{q=0}^{2\log n} \frac{4}{2^{q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_{q=0}^{2\log n} 8 = O(\log^3 n) y_{e'} 
+\end{align}
+
+So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.
+
+Using this, we can bound the probability that a particular edge $e$ of the original graph is included.
+For $e$ to be included, on one of the $\tau$ trials, the algorithm must chose some tree edge $e'$ such that $e' \in \text{map}^{-1}(e)$ (recall that this is the set of tree edges which, if selected, result in edge $e$ being included).
+So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$.
+Then we have the inequality
+\begin{align}
+ \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} 
+\end{align}
+The $\tau$ comes from a union bound over all trials. The $O(\log^3 n)y_{e'}$ comes from the first part of the proof, where we bounded the probability of including a specific $e'$.
+
+To simplify this inequality, we apply a series of definitions and lemmas stated earlier in Section~\ref{sec:rackestrees}.
+We can rewrite the quantity on the right-hand side as $O(\log^3 n) \tau E[load(e)]$ due to the definition of $load$.
+Using the definition of $rload$, this can be rewritten again as $O(\log^3 n) \tau E[rload(e) x_e']$.
+By  Lemma~\ref{lem:rload}, so we can bound this above by $O(\log^3 n) \tau \frac{4}{k} \alpha x_e$.
+Since $\alpha$ is bounded by $O( \log n)$, we get our final inequality of
+\begin{align}
+ \textbf{E}[X_e] &\leq \frac{O(\log^4 n)\tau}{k} x_e 
+\end{align}
+
+From here, we simply apply linearity of expectation to bound the total cost. We have 
+%
+%
+% Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
+%\begin{align}
+%X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
+%\end{align}
+%Because if $e$ is included in the graph, it must have come from some edge in the tree. 
+%\begin{align}
+% \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
+%        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
+%        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
+%        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
+%        & = \dfrac{O(\log^4 n)\tau}{k} x_e
+%\end{align}
+%So now, bounding the optimum, we get
+\begin{align}
+\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
+                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
+\end{align}
+So when $\tau = O(\log h + k)$, we get our desired approximation.
+\end{proof}
+
+\begin{figure}
+\label{fig:roundgkronnode}
+\centering
+\includegraphics[width=0.6\linewidth]{RoundGKRonNode.pdf}
+\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
+\end{figure}
+
+Having established that the expected cost is only a polylogarithmic factor away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.
+We will need the following definition.
+
+\subsection{Claim B}
 
@@
 \end{proof}
-
-\subsection{Claim B}
-
-\begin{lemma}[\cite{ssc}]
-$\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
-\end{lemma}
-
-\begin{proof}
-We prove this by bounding the probability that a given edge is included in $H$ by $O(\log^4n(\frac{\log h}{k} + 1))x_e$. The claim then follows by linearity of expectation.
-
-Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$.
-For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_t$ and some index $q \in [0,\dots,2\log n]$.
-For this to occur, $v$ must be $q$-marked, an event that occurs with probability $\frac{4}{2^{-q}}$.
-
-For a given edge $e'$, there are at most $height(T)$ ancestors, which means that there are at most $height(T)$ different vertices $v$ that, if $q$-marked, may lead to $e'$ being included.
-For each $v$, we must consider all $O(\log n)$ possible values of $q$.
-For each value of $q$, the probability of being $q$-marked is $\frac{4}{2^{-q}}$.
-Once the vertex is $q$-marked, we have $\tau'$ trials of the RoundGKR algorithm, where in each trial, there is a $2^{q+1}y_{e'}$ chance of edge $e'$ being included (by construction of the algorithm).
-Multiplying these probablities together and applying a union bound over all $\tau'$ trials and over all possible values of $q$, we get an upper bound of
-
-\begin{align}
-height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 = O(\log^3 n) y_{e'} 
-\end{align}
-
-So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.
-
-So now in order to include some edge $e$ of the graph $G$, we must include some edge $e' \in \text{map}^{-1}(e)$ (recall that this is the set of tree edges which, if selected, result in edge $e$ being included).
-So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$, and $Y_{e'}$ be the indicator random variable which says that edge $e'$ in the tree is included in some RoundGKR execution.
-Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
-\begin{align}
-X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
-\end{align}
-Because if $e$ is included in the graph, it must have come from some edge in the tree. 
-\begin{align}
- \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
-        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
-        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
-        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
-        & = \dfrac{O(\log^4 n)\tau}{k} x_e
-\end{align}
-So now, bounding the optimum, we get
-\begin{align}
-\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
-                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
-\end{align}
-So when $\tau = O(\log h + k)$, we get our desired approximation.
-\end{proof}
-
-\begin{figure}
-\label{fig:roundgkronnode}
-\centering
-\includegraphics[width=0.6\linewidth]{RoundGKRonNode.pdf}
-\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
-\end{figure}
-
-Having established that the expected cost is only a polylogarithmic factor away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.
-We will need the following definition.
-
 \bibliography{references}

### 2015-05-11 draft.tex
fixed proof

@@
 Using this, we can bound the probability that a particular edge $e$ of the original graph is included.
-For $e$ to be included, on one of the $\tau$ trials, the algorithm must chose some tree edge $e'$ such that $e' \in \text{map}^{-1}(e)$ (recall that this is the set of tree edges which, if selected, result in edge $e$ being included).
+For $e$ to be included, on one of the $\tau$ trials, the algorithm must chose some tree edge $e'$ such that $e' \in \mathrm{map}^{-1}(e)$ (recall that this is the set of tree edges which, if selected, result in edge $e$ being included).
 So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$.
@@
 \begin{align}
- \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} 
+ \textbf{E}_{R}[X_e] &\leq \tau \sum_{e' \in \mathrm{map}^{-1}(e)} O(\log^3 n) y_{e'} 
 \end{align}
-The $\tau$ comes from a union bound over all trials. The $O(\log^3 n)y_{e'}$ comes from the first part of the proof, where we bounded the probability of including a specific $e'$.
+where the expectation $\text{E}_{R}[X_e]$ is over the random choices of the algorithm, after choosing a R\"{a}cke tree.
+The $\tau$ comes from a union bound over all trials.
+The $O(\log^3 n)y_{e'}$ comes from the first part of the proof, where we bounded the probability of including a specific $e'$.
 
 To simplify this inequality, we apply a series of definitions and lemmas stated earlier in Section~\ref{sec:rackestrees}. 
-We can rewrite the quantity on the right-hand side as $O(\log^3 n) \tau E[load(e)]$ due to the definition of $load$.
-Using the definition of $rload$, this can be rewritten again as $O(\log^3 n) \tau E[rload(e) x_e']$.
-By  Lemma~\ref{lem:rload}, so we can bound this above by $O(\log^3 n) \tau \frac{4}{k} \alpha x_e$.
-Since $\alpha$ is bounded by $O( \log n)$, we get our final inequality of
+\begin{align}
+\textbf{E}_{\mathcal{D}}[E_{R}[X_e]] &\leq \textbf{E}_{\mathcal{D}}[\tau \sum_{e' \in \mathrm{map}^{-1}(e)} O(\log^3 n) y_{e'}] \\
+               &\leq O(\log^3 n) \tau \textbf{E}_{\mathcal{D}}[\sum_{e' \in \mathrm{map}^{-1}(e)} y_{e'}] \\
+               & \leq O(\log^3 n) \tau \textbf{E}_{\mathcal{D}}[load(e)]
+\end{align}
+where the expectation is over the choice of R\"{a}cke tree. Using the definition of $rload$, 
+\begin{align}
+\textbf{E}[X_e] &\leq O(\log^3 n) \tau E[rload(e) x_e'] \\
+                &\leq O(\log^3 n) \tau \frac{4}{k} \alpha x_e
+\end{align}
+where $\text{E}[X_e]$ is the expectation over both random choices of the algorithm as well as random choices of the R\"{a}cke tree.
+Lemma~\ref{lem:rload} gives a bound on the maximum relative load.
+$\alpha$ is bounded by $O( \log n)$, so our final inequality is
 \begin{align}

### 2015-05-12 draft.tex
added improvements

@@
 \begin{lemma}[\cite{ssc}]
+\label{lem:cost}
 $\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
@@
 \begin{lemma}[\cite{ssc}]
+\label{lem:connected}
 With probability at least $\frac{3}{4}$, all set pairs are at least $\frac{k}{16\alpha} + 1$ edge connected in $H$. 
@@
 \end{proof}
+
+\section{Potential Improvements}
+
+There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse.
+In the original algorithm, we must iterate through each $v \in V_T$ and run some RoundGKRrounds on its subtree.
+If there are multiple flow paths from different groups, say $(S_1', T_1')$ and $(S_2', T_2')$ going through $v$, then the original algorithm could find both at once.
+We could be finding $h$ paths with $O(\log n)$ cost (since running RoundGKR on each subtree makes each edge appear in $O(\log n)$ subtrees).
+
+If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small).
+We can run the algorithm without looking for the nodes where the flow paths turn.
+In particular, we could treat it as many different instances of the Group Steiner Tree problem.
+The algorithm would be:
+\begin{codebox}
+\li Set $H \leftarrow \emptyset$
+\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
+\li Let $x' \leftarrow x*\frac{4}{k}$. 
+\li Prepare $\mathcal{D}$ be the distribution of Racke tree embeddings for $G$ with $x'$.
+\li \For $\tau$ rounds \Do
+\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
+\li \For $q = 0, ..., 2\log n$ \Do
+\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
+\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
+\li \If $s$ is $q$-marked \Then
+\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
+\li \For $\tau'$ iterations, \Do
+\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
+\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
+\li return $H$
+\end{codebox}
+The main difference lies in line 8.
+Instead of iterating through all $v \in V_T$ to find where the flow path turns, we take advantage of knowing where the flow begins.
+We know all flow paths go from $S_i'$ to $T_i'$, so we make $s \in S_i'$ the root of the tree.
+It is unnecessary to look for where the flow turns.
+We still have to iterate through $q= 0, ..., 2\log n$, since the flow of at least $1$ between $S_i'$ and $T_i'$ might be divided among different flow paths starting at different nodes in $S_i'$.
+This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.
+
+Lemma~\ref{lem:connected} still holds. Since we know exactly where the flow paths must start.
+
+\begin{lemma}
+The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
+\end{lemma}
+
+\begin{proof}
+The proof is the same as the proof of Lemma~\ref{lem:cost}.
+The only difference is that instead of each edge being included in at most $height(T)$ RoundGKR steps, we include it in at most $S$ RoundGKR steps.
+\end{proof}
+
+Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
+Now the question becomes, can we reduce $S$ to $h$?
+One possible idea is to join all the nodes in $S_i'$.
+This would destroy the tree property for RoundGKR, but maybe we can disregard some cycles (at least if we analyzed the case with unit costs on the edges).
+\cite{ssc} uses RoundGKR and R\"{a}cke trees as black boxes, so maybe there is some hope.
+If this is possible, then our competitiveness would be $O(h\log^3n(\dfrac{\log h}{k} + 1))$.
+Now if $h = o(\log n)$, then we would prefer this algorithm.
+
 \bibliography{references}

### 2015-05-13 draft.tex
added related work and context section in response to nitya's reply to karger

@@
 
+\subsection{Overview}
+
 In this paper, we analyze the problem of Survivable Set Connectivity (SSC), a generalization of the classical Set Connectivity problem. Set connectivity is formulated as:
 \begin{quote}
-\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$. \\
+\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$. \\
 \textbf{Output}: A minimum cost subgraph $H \subset G$ such that there is a path between $S_i$ and $T_i$ for each $i$. 
@@
 Finally, we combine all these concepts together to present and analyze an approximation algorithm for SSC.
-%
-%[ GIVE MORE EXAMPLES HERE ]
-%
-%As with many of these kinds of problems, SSC is $\mathsf{NP}$-hard.
-The common route taken in 6.856 has been to find polynomial time algorithms for approximations; however, in the case with SSC, it is $\mathsf{NP}$-hard to achieve a polylogarithmic approximation.
-%
-%Another possible approach is therefore to relax the question.
-Instead of requiring at least $k$ edge-disjoint paths, we will allow some sets to have less than $k$ paths, but not too much less.
-We will present an approximation algorithm which outputs a subgraph of cost $O(polylog(n))$ times the optimum such that for each $(S_i, T_i)$ pairs, there are at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths between $S_i$ and $T_i$.
-%
-%The approximation algorithm will follow the usual approach to approximation algorithms of this kind.
-We will first write the problem as an integer linear program, we solve the linear programming relaxation, and then we round the solution.
-%
-%The analysis will be slightly different from the analysis shown in class.
-Usually, our randomized algorithm will return a feasible solution to the problem, and our analysis work is mostly to bound the cost.
-This was the case with max-sat, set-cover, and multi-commodity flows.
-In our case, we will show that the rounded solution will be close to the optimal, but we will work to show that the rounded solution is feasible.
+
+\subsection{Related Work and Context}
+
+The paper by Chalermsook et al.
+is the first and (currently) only paper to consider the Survivable Set Connectivity problem \cite{ssc}.
+Therefore, we survey the only known approximation algorithm for the problem.
+Chalermsook et al.
+noted that the original Set Connectivity problem has a large body of prior work, but they found that the best techniques for solving Set Connectivity do not translate to the Survivable variant of the problem.
+Thus, we present Survivable Set Connectivity as a standalone problem, despite its obvious similarities to Set Connectivity.
+
+At this time, it seems that Survivable Set Connectivity is only interesting from a theoretical standpoint, as a ``natural" generalization of Set Connectivity.
+It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.
 

### 2015-05-13 draft.tex
small changes in intro

@@
 \begin{quote}
-\textbf{Input}: A graph weighted $G = (V, E)$, $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
+\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
 \textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
@@
 
-At this time, it seems that Survivable Set Connectivity is only interesting from a theoretical standpoint, as a ``natural" generalization of Set Connectivity.
+At this time, it seems that Survivable Set Connectivity is motivated primarily by theoreitcal interest, as a ``natural" generalization of Set Connectivity.
 It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.

### 2015-05-13 draft.tex
added expository text to beginning of rackes trees section in response to nityas comments. also fixed the dots above the a in the word racke

@@
 
-We will use a particular type of tree embedding given in \cite{racke} which will allow us to map paths in the tree to paths in the graph.
+In this section, we introduce a specific type of \emph{tree embedding}.
+A tree embedding is a transformation that takes general graphs and maps them to trees, while preserving much of the information present in the original graph.
+This way, algorithmic procedures that work well on trees can be applied to general graphs after a tree embedding has been applied.
+
+For the SSC problem, we will use a specific tree embedding formulated by R\"{a}cke, known as R\"{a}cke's trees.
+The property we are most interested in is the way that R\"{a}cke's tree embeddings preserve flow properties in the original graph.
+The definition of these embeddings is as follows.
 
@@
 Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices.
-This gives us a simple way to map flows from Racke trees to the graph and vice-versa.
+This gives us a simple way to map flows from R\"{a}cke's trees to the graph and vice-versa.
 
@@
 
-There are some crucial properties of Racke trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to [CITE] for the proofs.
+There are some crucial properties of R\"{a}cke's trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to [CITE] for the proofs.
 
@@
 \label{lem:rload}
-For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}^{\geq 0}$, we can sample efficiently from Racke trees of $G$, such that 
+For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}^{\geq 0}$, we can sample efficiently from R\"{a}cke's trees of $G$, such that 
 \begin{align}
@@
 \li Let $x' \leftarrow x*\frac{4}{k}$. 
-\li Prepare $\mathcal{D}$ be the distribution of Racke tree embeddings for $G$ with $x'$.
+\li Prepare $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
 \li \For $\tau$ rounds \Do
@@
 
-Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$.
+Let $(T = (V_t, E_t), y, \text{map})$ be a R\"{a}cke's tree sampled from $\mathcal{D}$.
 For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_t$ and some index $q \in [0,\dots,2\log n]$.
@@
 
-So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.
+So the probability that a given edge of the tree is included in a particular sampling of a R\"{a}cke's tree is $O(\log^3 n) y_{e'}$.
 
@@
 \li Let $x' \leftarrow x*\frac{4}{k}$. 
-\li Prepare $\mathcal{D}$ be the distribution of Racke tree embeddings for $G$ with $x'$.
+\li Prepare $\mathcal{D}$, the distribution of R'\"{a}cke's tree embeddings for $G$ with $x'$.
 \li \For $\tau$ rounds \Do

### 2015-05-13 draft.tex
fixed typo

@@
 \text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{for each }S\text{ where } S_i \subset S,T_i \subset V - S, \\ & \hspace{1in}\delta(S) \text{ is the edges of the $S$ cut } \\
-& x_e \in [0,1] \text{ for all }e \in E
+& x_e \in \{0,1\} \text{ for all }e \in E
 \end{align}
@@
 Of course, since this is an integer linear program, we must relax it to fractional solutions in order to solve it.
-Thus, we relax the constraint of $x_e \in [0,1]$ to $0 \leq x_e \leq 1$.
+Thus, we relax the constraint of $x_e \in \{0,1\}$ to $0 \leq x_e \leq 1$.
 However, there is still a slight issue; there can be exponentially many constraints.

### 2015-05-13 draft.tex
referencing image

@@
 
-\begin{figure}
-\centering
-\label{fig:rackecut}
-\includegraphics[width=0.5\linewidth]{Rackecut.pdf}
-\caption{R\"{a}cke's tree cut induced by an edge in the tree.}
-\end{figure}
-
 \begin{definition}
@@
 
+Figure~\ref{fig:racketree} shows an example R\"{a}cke's tree.
+We see a tree on the left-hand side which corresponds to the graph on the right-hand side.
+Each node is labeled by a number.
+The number indicates the projection of $\mathrm{map}$.
+A node of the tree labeled $1$ corresponds to the node in the graph labeled $1$.
+As you can see, the leaves are in bijection with the nodes of the graph.
+
+In addition, edges in the tree correspond to paths in the graph.
+The bolded edges of the tree map to the bolded edges in the graph.
+The top-most edge in the tree connects nodes $3$ and $5$, and that edge maps to the edge in the graph connecting $3$ and $5$.
+Then the bolded edge in the tree connecting $5$ to $5$ corresponds to the empty path.
+The bolded edge of the tree connecting $5$ to $4$ corresponds to the bolded edge in the graph connecting $4$ and $5$.
+Paths in the tree correspond to paths in the graph.
+
+We also note the capacity of the edge in the tree labeled $y$ is $x_1 + x_2 + x_3$.
+Edge $y$ disconnects the leaves into two groups, $S'$ and the rest.
+$S'$ maps bijectively to $S$.
+$S$ induces a cut on the graph, which cuts edges $x_1$, $x_2$, and $x_3$.
+Therefore, the capacity of $y$ (as defined by R\"{a}cke's trees) is the sum of the capacities of $x_1,x_2,$ and $x_3$.
+
+Another thing to notice is that $load(x_1) = 0$, since $\mathrm{map}^{-1}(x_1) = \emptyset$.
+An immediate consequence, which we can see from the load is that removing an edge with load 0 does not affect the connectivity of the graph.
+At a high level, the load will measure how necessary an edge is for connectivity.
+
+\begin{figure}
+\label{fig:racketree}
+\includegraphics[width=\linewidth]{RackeTree.pdf}
+\caption{A R\"{a}cke's tree example.
+A R\"{a}cke tree on the left maps to a graph on the right.
+The map on vertices is defined by the labelings on the nodes.
+The bolded edges map to the bolded edges.
+Edge $y$ defines a set of leaves $S'$, which defines a cut on the graph, $S$.
+$S$ cuts edges $x_1, x_2,$ and $x_3$; therefore, $y = x_1 + x_2 + x_3$.}
+\end{figure}
+
 The usefulness of R\"{a}cke's trees becomes apparent when we consider multi-commodity flows.
@@
 
-Figure~\ref{fig:racketree} gives an example of the flow correspondence between a graph and it's associated R\"{a}cke's tree.
-Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices.
-This gives us a simple way to map flows from R\"{a}cke's trees to the graph and vice-versa.
-
-\begin{figure}
-\label{fig:racketree}
-\centering
-\includegraphics[width=0.8\linewidth]{Rackeembeddinggraph.pdf}
-\caption{Example Racke Tree where red nodes are mapped and edge maps to a path.}
-\end{figure}
-
-There are some crucial properties of R\"{a}cke's trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to [CITE] for the proofs.
+There are some crucial properties of R\"{a}cke's trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to \cite{racke} for the proofs.
 
@@
 
-The important property of the algorithm can be summarized in the following lemma, whose proof can be found in [CITE].
+The important property of the algorithm can be summarized in the following lemma, whose proof can be found in \cite{GKR}.
 
@@
 \li Let $x' \leftarrow x*\frac{4}{k}$. 
-\li Prepare $\mathcal{D}$, the distribution of R'\"{a}cke's tree embeddings for $G$ with $x'$.
+\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
 \li \For $\tau$ rounds \Do

### 2015-05-13 draft.tex
finished revising the intro

--- 2015-05-13 draft.tex
@@
 \begin{quote}
-\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}$ and a collection of sets $(S_i, T_i)$. \\
-\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there is a path between $S_i$ and $T_i$ for each $i$. 
+\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}$ and a collection of tuples of the form $(S_i, T_i)$.
+Each $(S_i,T_i)$ is a pair of disjoint vertex subsets.
+\\
+\textbf{Output}: A minimum cost subgraph $H \subseteq G$ such that there is a path between $S_i$ and $T_i$ for each $i$. 
 \end{quote}
+
+Note that a ``path between $S_i$ and $T_i$" refers to any path that connects a vertex in $S_i$ to a vertex in $T_i$.
+
 In SSC, the problem is modified so that each pair of sets $(S_i,T_i)$ must be connected by $k_i$ paths, instead of just 1. More formally, the problem is:
@@
 \begin{quote}
-\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of sets $(S_i, T_i)$, along with a value $k$. \\
-\textbf{Output}: A minimum cost subgraph $H \subset G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
+\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of tuples of the form $(S_i, T_i)$, along with a value $k$.
+Again, each $(S_i,T_i)$ is a pair of disjoint vertex subsets.
+\\
+\textbf{Output}: A minimum cost subgraph $H \subseteq G$ such that there are $k$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$. 
 \end{quote}
@@
 Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem given in \cite{ssc}.
-Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths.
+Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths, where $n = |V|$.
 With this relaxation, it is possible to find a subgraph with cost $O(polylog(n))$ times the optimum.
@@
 The paper is organized as follows.
-We first present a natural integer linear programming formulation of the problem.
-Then, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm.
-We also show a general rounding scheme, called RoundGKR, which our algorithm uses as a black box.
-Finally, we combine all these concepts together to present and analyze an approximation algorithm for SSC.
+Sections 2, 3, and 4 provide the background necessary to understand the algorithm by Chalermsook et al.
+In Section 2, we present a natural integer linear programming formulation of the problem.
+Then, in Section 3, we introduce the idea of a \emph{tree embedding}, which allows us to transform arbitrary graphs $G$ into trees that can be more easily handled by the algorithm.
+In Section 4, we give a rounding scheme by Garg et al.
+known as RoundGKR, which the algorithm uses as a black box \cite{GKR}.
+We then pull together these concepts in Section 5 to present and analyze the approximation algorithm for SSC by Chalermsook et al.
+Finally, in Section 6, we present an algorithm of our own that slightly improves upon the approximation ratio given by Chalermsook et al.
 
@@
 Chalermsook et al.
-noted that the original Set Connectivity problem has a large body of prior work, but they found that the best techniques for solving Set Connectivity do not translate to the Survivable variant of the problem.
+noted that the original Set Connectivity problem has a large body of prior work, but they found that the best techniques for solving Set Connectivity do not translate to the survivable variant of the problem.
 Thus, we present Survivable Set Connectivity as a standalone problem, despite its obvious similarities to Set Connectivity.

### 2015-05-13 draft.tex
fixed a typo in 1.2

@@
 
-At this time, it seems that Survivable Set Connectivity is motivated primarily by theoreitcal interest, as a ``natural" generalization of Set Connectivity.
+At this time, it seems that Survivable Set Connectivity is motivated primarily by theoretical interest, as a ``natural" generalization of Set Connectivity.
 It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.

### 2015-05-13 draft.tex
intro small changes

@@
 \begin{quote}
-\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}$ and a collection of tuples of the form $(S_i, T_i)$.
+\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of tuples of the form $(S_i, T_i)$.
 Each $(S_i,T_i)$ is a pair of disjoint vertex subsets.
@@
 We then pull together these concepts in Section 5 to present and analyze the approximation algorithm for SSC by Chalermsook et al.
-Finally, in Section 6, we present an algorithm of our own that slightly improves upon the approximation ratio given by Chalermsook et al.
+Finally, in Section 6, we present a slight modification to the algorithm which improves the approximation ratio under special circumstances.
+We also conclude with ideas for further improvements.
 

### 2015-05-13 draft.tex
not sure what changes i made
minor changes to intro

@@
 
-Note that a ``path between $S_i$ and $T_i$" refers to any path that connects a vertex in $S_i$ to a vertex in $T_i$.
+Note that a ``path between $S_i$ and $T_i$" refers to any path that connects a vertex in $S_i$ to a vertex in $T_i$. The cost of a subgraph is simply the sum of the cost of the subgraph edges.
 
@@
 We then pull together these concepts in Section 5 to present and analyze the approximation algorithm for SSC by Chalermsook et al.
-Finally, in Section 6, we present a slight modification to the algorithm which improves the approximation ratio under special circumstances.
-We also conclude with ideas for further improvements.
+Finally, in Section 6, we present our own modification to the algorithm which improves the approximation ratio under special circumstances.
+We also conclude with ideas for potential further improvements.
 
@@
 The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut.
-This property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
+We claim (but do not prove) that this property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
 %

### 2015-05-13 draft.tex
finished section 2

@@
 \end{align}
-Thus, our output $H$ will be the subgraph consisting of edges $e$ where $x_e = 1$. \\ \\
-
-We claim that the following ILP captures SSC exactly. 
-SSC-LP:
+Thus, our output $H$ will be the subgraph consisting of edges $e$ where $x_e = 1$.
+Also, for a graph $G = (V,E)$ and for a set $S \subseteq V$, we define $\delta(S)$ to be the set of edges crossing the cut from $S$ to $V \setminus S$.
+With this setup, we claim that the following ILP captures SSC exactly. 
 \begin{align}
 \min & \sum c(x) x_e  \\
-\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{for each }S\text{ where } S_i \subset S,T_i \subset V - S, \\ & \hspace{1in}\delta(S) \text{ is the edges of the $S$ cut } \\
+\text{ s.t } & \sum_{e \in \delta(S)} x_e \geq k, \text{for each }S\text{ where } S_i \subset S,T_i \subset V \setminus S,  \\
 & x_e \in \{0,1\} \text{ for all }e \in E
@@
 We claim (but do not prove) that this property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
-%
-%
-% 
-%This cut-based integer linear program finds exactly $H$.
-To see why the constraints ensure that each $(S_i, T_i)$ pair has at least $k$ edge disjoint paths, we can look at the cuts corresponding to $S_i$ and $T_i$.
-First, we let $S = S_i$, then there are $k$ outgoing edges.
-We can choose to include one more node to $S$, following a particular outgoing edge of the cut in $H$.
-We can continue doing this until we reach $T_i$.
-This will trace out a path between $S_i$ and $T_i$.
-If we do this for each edge, and then we do this for each $(S_i, T_i)$ pair, we can confirm that there are in fact $k$ edge-disjoint paths between each $(S_i, T_i)$ pair.
 
-Of course, since this is an integer linear program, we must relax it to fractional solutions in order to solve it.
-Thus, we relax the constraint of $x_e \in \{0,1\}$ to $0 \leq x_e \leq 1$.
-However, there is still a slight issue; there can be exponentially many constraints.
-This is because there are exponentially many choices of $S$ for each $(S_i,T_i)$ pair.
-To get around this issue, we note that the ellipsoid algorithm can handle linear programs with arbitrarily many constraints, as long as it is given a separation oracle.
-Luckily, we can give such an oracle.
+Of course, since this is an integer linear program, our best hope is to approximate it.
+We relax the program to fractional solutions, so the constraint that $x_e \in \{0,1\}$ becomes $0 \leq x_e \leq 1$.
+However, there is still a slight issue; we have exponentially many constraints.
+This occurs because there can be exponentially many choices of $S$ for each $(S_i,T_i)$ pair.
+To get around this issue, we note that the ellipsoid algorithm can handle linear programs with arbitrarily many constraints, as long as it is given a polynomial time separation oracle.
+Luckily, such an oracle exists and we sketch it here.
 
-The separation oracle just computes the minimum $S_i, T_i$ cut in the graph.
-What we can do is contract $S_i$ and $T_i$ to single vertices, and then compute the min-cut in the remaining graph.
+The oracle computes the minimum $S_i, T_i$ cut in the graph.
+It contracts $S_i$ and $T_i$ to single vertices, and then computes the min-cut in the remaining graph.
 If there is a min-cut of size less than $k$, then that cut will correspond to a violating contraint.
-If the min-cut has size at least $k$, then all cuts have size at least $k$, so we have satisfied the constraints.
+If the min-cut has size at least $k$, then all cuts have size at least $k$, so all constraints are satisfied.
 

### 2015-05-13 draft.tex
added guiding text to claim b

--- 2015-05-13 draft.tex
@@
 
-Intuitively, bad sets correspond to sets which are necessary in the graph. We want graphs to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity.
+Intuitively, bad sets correspond to sets which are necessary in the graph.
+We want graphs to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity even if we remove them.
 
@@
 
-\textbf{Proof Idea}:
+\textbf{Proof Idea of Lemma~\ref{lem:connected}}:
 \begin{enumerate}
@@
 \item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$.
-This flow must go up the tree to some common ancestor $v$ and then back down.
+Each flow path must go up the tree to some common ancestor $v$ and then back down.
 \item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
@@
 
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{lem:connected}]
 We fix an $F$ of size at most $\frac{k}{16\alpha}$ and an $i$ and show that $(S_i, T_i)$ are connected with an edge outside of $F$.
@@
 So the probability of failure is $(1-\beta)$.
-If we repeat this $\tau = \frac{1}{\beta}\ln(4hn^{\frac{k}{16\alpha}})$ times, then our failure probability goes down to $\dfrac{1}{4hn^{\frac{k}{16\alpha}}}$.
+If we repeat this $\tau = \frac{1}{\beta}\ln(4hn^{\frac{k}{16\alpha}}) = O(\log h + k)$ times, then our failure probability goes down to $\dfrac{1}{4hn^{\frac{k}{16\alpha}}}$.
 So now we take the union bound over all of $F$ and over all $i$, so we get probability of failure at most $\frac{1}{4}$.
@@
 \end{proof}
+
+As of right now, we have shown steps $1$, $2$ and $5$ in the proof idea of Lemma~\ref{lem:connected}. We finish the proof by showing steps $3$ and $4$.
 
@@
 
-Now for some reason, when we remove a total capacity of $\frac{1}{2}$, we are left with a flow of $2 - \frac{1}{2} = \frac{3}{2}$.
+Removing the total capacity of $\frac{1}{2}$, we are left with a flow of $2 - \frac{1}{2} = \frac{3}{2}$.
 In particular, we can support a unit flow from $S_i'$ to $T_i'$.
 That unit flow can be decomposed into paths $P_1, ..., P_z$, disregarding paths with very small amount of flow $(\leq \frac{1}{2n^2})$.
-So each path goes up from a leaf, turns at some $v$, and then goes down to another leaf.
+Each flow path goes up from a leaf, turns at some $v$, and then goes down to another leaf.
 Let $\phi_v$ be the flow turning at $v$.
+Let $\phi_v$ be the total flow turning at node $v$.
 
 Since we support a flow of at least $\frac{3}{2}$ and we removed paths with at most $\frac{1}{2n^2}$ flow, we are left with
-\[ \phi_v \geq \frac{3}{2} - \dfrac{1}{2n^2}|E_T] \geq 1 \]
+\[ \sum_{v \in V_t} \phi_v \geq \frac{3}{2} - \dfrac{1}{2n^2}|E_t| \geq 1 \]
 Now $\phi_v$ falls between some $(2^{-q_v-1}, 2^{-q_v}]$ for some $q_v \in \{0, ..., 2\log_2 n\}$.
-Now the probability that none of the $v \in V_T$ is $q$-marked exactly at $q_v$ when we have a good embedding is at most $e^{-3/4}$ which follows by a Chernoff bound.
-So conditioning on this happening, the path gets multiplied by $2^{q_v+1}$ and so it supports a flow of $1$.
-Now Lemma~\ref{lem:findpath} says the path will be included with probability at least $1 - (1 - \Omega(1/\log n))^{\tau'}$.
-If we let $\tau' = O(\log n)$, then we get any constant probability $\epsilon$.
+Now the probability that none of the $v \in V_t$ is $q$-marked exactly at $q_v$ when we have a good embedding is at most $e^{-3/4}$ which follows by a Chernoff bound.
+The important thing to note is that each time we try to $q$-mark a node, it is an independent event.
+The expected value of the number of vertices that get $q$-marked at $q_v$ is at least $4$ and we need at least $1$.
+These values are sums of independent random variables, so we can apply the Chernoff bound.
+
+Conditioning on finding one such $v$, the path gets multiplied by $2^{q_v+1}$.
+Now it supports a flow of $1$.
+Lemma~\ref{lem:findpath} says the path will be included with probability at least $\Omega(\frac{1}{\log n})$ in a single round of RoundGKR.
+So if we repeat it $\tau'$ times, the probability we do not find the path is $1 - (1 - \Omega(1/\log n))^{\tau'}$.
+Letting $\tau' = O(\log n)$, we get any constant probability $\epsilon$.
 Since we need to find both paths from the root to both leaves, we get a failure probability of $2\epsilon$.
@@
 \end{proof}
+
+This concludes steps $3$ and $4$ of the proof idea for Lemma~\ref{lem:connectivity}.
+This finishes the proof that after running the rounding algorithm, each $(S_i, T_i)$ tuple will have $\Omega(\frac{k}{\log n})$ paths connecting $S_i$ to $T_i$.
 

### 2015-05-13 draft.tex
added other observation

@@
 Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
+Along similar lines, if $\sum_{i \in [h]} |T_i| = T$ is small, then we could compress the R\"{a}cke tree to contain only the leaves we want.
+If $T = O(\log n)$, then the tree could be compressed to size $O(\log n)$, and so we would find unit flow paths with probability $\Omega(\frac{1}{\log \log n})$.
+This means we could reduce $\tau'$ to $O(\log \log n)$ and decrease our approximation ratio.
+
 Now the question becomes, can we reduce $S$ to $h$?

### 2015-05-13 draft.tex
changes to section 3

--- 2015-05-13 draft.tex
@@
 In this section, we introduce a specific type of \emph{tree embedding}.
-A tree embedding is a transformation that takes general graphs and maps them to trees, while preserving much of the information present in the original graph.
-This way, algorithmic procedures that work well on trees can be applied to general graphs after a tree embedding has been applied.
+A tree embedding is a transformation that takes general graphs and maps them to trees, while preserving specific information present in the original graph.
+This way, algorithmic techinques that work well on trees can be applied to general graphs after a tree embedding has been applied.
 
-For the SSC problem, we will use a specific tree embedding formulated by R\"{a}cke, known as R\"{a}cke's trees.
+For the SSC problem, we will use a specific tree embedding formulated by R\"{a}cke, known as R\"{a}cke's trees \cite{racke}.
 The property we are most interested in is the way that R\"{a}cke's tree embeddings preserve flow properties in the original graph.
@@
 \begin{definition}
-For a given graph $G = (V, E)$ with edge capacities $x_e \geq 0$, $e \in E$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ of $T$, and $\mathrm{map}$ is a function $V_T \cup E_T \to V \cup 2^E$ satisfying the following properties:
+For a given graph $G = (V, E)$ with edge capacities $x_e \geq 0$ for all $e \in E$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ (with $y_e \geq 0$ for all $e \in E_T$), and $\mathrm{map}$ is a function that maps vertices in $V_T$ to vertices in $V$, and edges in $E_T$ to sets of edges in $E$.
+The following properties must also hold:
 \begin{enumerate}
-\item For each node $v \in V_T$, $\mathrm{map}(v) \in V$. Thus, the $\mathrm{map}$ function maps nodes in the tree $T$ to nodes in the original graph, $G$.
-\item Furthermore, $\mathrm{map}$ restricted to the leaves of $T$ is a bijection with the vertices of $G$.
+\item For each node $v \in V_T$, $\mathrm{map}(v) \in V$.
+Furthermore, $\mathrm{map}$ restricted to the leaves of $T$ is a bijective function whose image contains all vertices of $G$.
 In other words, each leaf of the tree $T$ is in one-to-one correspondence with a vertex of the original graph, $G$.
@@
 
-Intuitively, bad sets correspond to sets which are necessary in the graph.
-We want graphs to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity even if we remove them.
+Intuitively, bad sets correspond to sets which are necessary in the graph. We want graphs to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity.
 
@@
 
-\textbf{Proof Idea of Lemma~\ref{lem:connected}}:
+\textbf{Proof Idea}:
 \begin{enumerate}
@@
 \item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$.
-Each flow path must go up the tree to some common ancestor $v$ and then back down.
+This flow must go up the tree to some common ancestor $v$ and then back down.
 \item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
@@
 
-\begin{proof}[Proof of Lemma~\ref{lem:connected}]
+\begin{proof}
 We fix an $F$ of size at most $\frac{k}{16\alpha}$ and an $i$ and show that $(S_i, T_i)$ are connected with an edge outside of $F$.
@@
 So the probability of failure is $(1-\beta)$.
-If we repeat this $\tau = \frac{1}{\beta}\ln(4hn^{\frac{k}{16\alpha}}) = O(\log h + k)$ times, then our failure probability goes down to $\dfrac{1}{4hn^{\frac{k}{16\alpha}}}$.
+If we repeat this $\tau = \frac{1}{\beta}\ln(4hn^{\frac{k}{16\alpha}})$ times, then our failure probability goes down to $\dfrac{1}{4hn^{\frac{k}{16\alpha}}}$.
 So now we take the union bound over all of $F$ and over all $i$, so we get probability of failure at most $\frac{1}{4}$.
@@
 \end{proof}
-
-As of right now, we have shown steps $1$, $2$ and $5$ in the proof idea of Lemma~\ref{lem:connected}. We finish the proof by showing steps $3$ and $4$.
 
@@
 
-Removing the total capacity of $\frac{1}{2}$, we are left with a flow of $2 - \frac{1}{2} = \frac{3}{2}$.
+Now for some reason, when we remove a total capacity of $\frac{1}{2}$, we are left with a flow of $2 - \frac{1}{2} = \frac{3}{2}$.
 In particular, we can support a unit flow from $S_i'$ to $T_i'$.
 That unit flow can be decomposed into paths $P_1, ..., P_z$, disregarding paths with very small amount of flow $(\leq \frac{1}{2n^2})$.
-Each flow path goes up from a leaf, turns at some $v$, and then goes down to another leaf.
+So each path goes up from a leaf, turns at some $v$, and then goes down to another leaf.
 Let $\phi_v$ be the flow turning at $v$.
-Let $\phi_v$ be the total flow turning at node $v$.
 
 Since we support a flow of at least $\frac{3}{2}$ and we removed paths with at most $\frac{1}{2n^2}$ flow, we are left with
-\[ \sum_{v \in V_t} \phi_v \geq \frac{3}{2} - \dfrac{1}{2n^2}|E_t| \geq 1 \]
+\[ \phi_v \geq \frac{3}{2} - \dfrac{1}{2n^2}|E_T] \geq 1 \]
 Now $\phi_v$ falls between some $(2^{-q_v-1}, 2^{-q_v}]$ for some $q_v \in \{0, ..., 2\log_2 n\}$.
-Now the probability that none of the $v \in V_t$ is $q$-marked exactly at $q_v$ when we have a good embedding is at most $e^{-3/4}$ which follows by a Chernoff bound.
-The important thing to note is that each time we try to $q$-mark a node, it is an independent event.
-The expected value of the number of vertices that get $q$-marked at $q_v$ is at least $4$ and we need at least $1$.
-These values are sums of independent random variables, so we can apply the Chernoff bound.
-
-Conditioning on finding one such $v$, the path gets multiplied by $2^{q_v+1}$.
-Now it supports a flow of $1$.
-Lemma~\ref{lem:findpath} says the path will be included with probability at least $\Omega(\frac{1}{\log n})$ in a single round of RoundGKR.
-So if we repeat it $\tau'$ times, the probability we do not find the path is $1 - (1 - \Omega(1/\log n))^{\tau'}$.
-Letting $\tau' = O(\log n)$, we get any constant probability $\epsilon$.
+Now the probability that none of the $v \in V_T$ is $q$-marked exactly at $q_v$ when we have a good embedding is at most $e^{-3/4}$ which follows by a Chernoff bound.
+So conditioning on this happening, the path gets multiplied by $2^{q_v+1}$ and so it supports a flow of $1$.
+Now Lemma~\ref{lem:findpath} says the path will be included with probability at least $1 - (1 - \Omega(1/\log n))^{\tau'}$.
+If we let $\tau' = O(\log n)$, then we get any constant probability $\epsilon$.
 Since we need to find both paths from the root to both leaves, we get a failure probability of $2\epsilon$.
@@
 \end{proof}
-
-This concludes steps $3$ and $4$ of the proof idea for Lemma~\ref{lem:connectivity}.
-This finishes the proof that after running the rounding algorithm, each $(S_i, T_i)$ tuple will have $\Omega(\frac{k}{\log n})$ paths connecting $S_i$ to $T_i$.
 

### 2015-05-13 draft.tex
changes to end of section 1

@@
 known as RoundGKR, which the algorithm uses as a black box \cite{GKR}.
-We then pull together these concepts in Section 5 to present and analyze the approximation algorithm for SSC by Chalermsook et al.
-Finally, in Section 6, we present our own modification to the algorithm which improves the approximation ratio under special circumstances.
-We also conclude with ideas for potential further improvements.
+We then pull together these concepts in Section 5 to present the approximation algorithm for SSC by Chalermsook et al.
+In Section 6, we analyze the performance of the algorithm.
+In Section 7, we present our own ideas for how the algorithm might be modified to improve its approximation ratio under special circumstances.
 

### 2015-05-13 draft.tex
aprpoximate nphard and remove claim but notprove

@@
 
-Unfortunately, solving exact Survivable Set Connectivity is $\mathsf{NP}$-hard \cite{ssc}.
+Unfortunately, even approximating Survivable Set Connectivity is $\mathsf{NP}$-hard \cite{ssc}.
 Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem given in \cite{ssc}.
@@
 The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut.
-We claim (but do not prove) that this property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
+This property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
 

### 2015-05-13 draft.tex
changes to racke tree section, made definition much longer

--- 2015-05-13 draft.tex
@@
 Note that $\mathrm{map}(u)$ and $\mathrm{map}(v)$ are vertices in $G$, so $\mathrm{map}(e)$ specifies a set of edges in $G$.
-%\item For some edge $e \in E_T$, $y_e$ (the cost of the edge) is a special quantity.
-Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$.
-Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
-%\begin{align}
-%y_e &= \sum_{e' \in \delta(S)} x_e
-%\end{align}
+\item The edge capacities, $y_e$, must be set by the following procedure: The removal of $e$ from $T$ separates the tree into two connected components.
+Let $S$ be the set of vertices of $G$ mapped to by the leaves of one of the connected components, and so $V \setminus S$ is the set of vertices of $G$ mapped to by the leaves of the other connected component.
+Recall that $\delta(S)$ is the set of edges in $E$ that cross from $S$ to $V \setminus S$.
+Then we set $y_e = \sum_{e' \in \delta(S)} x_{e'}$, the total edge capacity crossing the cut.
 \end{enumerate}
@@
 
-With this setup, we can define the inverse function, $\mathrm{map}^{-1}$.
-If we try to compute $\mathrm{map}^{-1}(v)$ for some $v \in V$, we note that multiple vertices in $T$ could map to $v$.
+We point out a small possibility for confusion here.
+We think of a Racke's tree embedding as a transformation from a graph to a tree, but the $\mathrm{map}$ function used in the above definition is a function from the tree to the graph.
+Thus, the function that actually \emph{embeds} the graph into the tree is the inverse function, $\mathrm{map}^{-1}$.
+
+Thus, we clarify the properties of $\mathrm{map}^{-1}$.
+If we apply $\mathrm{map}^{-1}$ to a node in the original graph, $v \in V$, we note that multiple vertices in $T$ could map to $v$.
 Thus, we specify that $\mathrm{map}^{-1}(v)$ be the unique \emph{leaf} vertex in $V_T$ that maps to $v$.
-We will also consider $\mathrm{map}^{-1}$ applied to sets of vertices $W \subseteq V$, and we define it in the obvious way: $\mathrm{map}^{-1}(W) = \bigcup_{v \in W} \mathrm{map}^{-1}(v)$.
+Recall that this uniqueness follows from the bijection property outlined in the above definition.
+We also consider $\mathrm{map}^{-1}$ applied to sets of vertices $W \subseteq V$, and we define it in a natural fashion: $\mathrm{map}^{-1}(W) = \bigcup_{v \in W} \mathrm{map}^{-1}(v)$.
 
-For edges $e = (u,v) \in E$, we define $\mathrm{map}^{-1}(e) = \{ f \in E_T | e \in \mathrm{map}(f)\}$.
-This is simply the set of all edges $f$ in the tree $T$ that get mapped to a set of edges $\mathrm{map}(f)$ that contain $e$.
-Again, this defintiion can be extended to sets of edges $F \subseteq E$, so that $\mathrm{map}^{-1}(F) = \bigcup_{e \in F} \mathrm{map}^{-1}(e)$.
-
-Finally, for an edge $e \in E_T$, we define $y_e$ as follows.
-The removal of $e$ from $T$ separates the tree into two connected components.
-Let $S$ be the set of vertices of $G$ mapped to by the leaves of one of the connected components, and so $V \setminus S$ is the set of vertices of $G$ mapped to by the leaves of the other connected component.
-Define $\delta(S)$ to be the set of edges in $E$ that cross from $S$ to $V \setminus S$.
-Then we set $y_e = \sum_{e' \in \delta(S)} x_{e'}$, the total edge capacity crossing the cut.
+For edges in the original graph, $e \in E$, we define $\mathrm{map}^{-1}(e) = \{ f \in E_T | e \in \mathrm{map}(f)\}$.
+This is simply the set of all edges $f$ in the tree $T$ that get mapped to a set of edges $\mathrm{map}(f) \subseteq E$ that contain $e$.
+Again, this definition can be extended to sets of edges $F \subseteq E$, so that $\mathrm{map}^{-1}(F) = \bigcup_{e \in F} \mathrm{map}^{-1}(e)$.
 

### 2015-05-13 draft.tex
finished the rackes trees section

@@
 \begin{quote}
-\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of tuples of the form $(S_i, T_i)$.
+\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of $h$ tuples of the form $(S_i, T_i)$.
 Each $(S_i,T_i)$ is a pair of disjoint vertex subsets.
@@
 \begin{quote}
-\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of tuples of the form $(S_i, T_i)$, along with a value $k$.
+\textbf{Input}: A weighted graph $G = (V, E)$, with edge cost function $c: E \rightarrow \mathbb{R}^{\geq 0}$ and a collection of $h$ tuples of the form $(S_i, T_i)$, along with a value $k$.
 Again, each $(S_i,T_i)$ is a pair of disjoint vertex subsets.
@@
 The definition of these embeddings is as follows.
+(\emph{Note to the reader:} the following definitions are quite long, so it may be helpful to reference Figure 1 on the following page while reading the definitions.)
 
@@
 We point out a small possibility for confusion here.
-We think of a Racke's tree embedding as a transformation from a graph to a tree, but the $\mathrm{map}$ function used in the above definition is a function from the tree to the graph.
+We think of a R\"{a}cke's tree embedding as a transformation from a graph to a tree, but the $\mathrm{map}$ function used in the above definition is a function from the tree to the graph.
 Thus, the function that actually \emph{embeds} the graph into the tree is the inverse function, $\mathrm{map}^{-1}$.
@@
 
-\begin{definition}
-Given a R\"{a}cke tree, the load on an edge of the graph $e \in E$ is
-\begin{align}
-load(e) &= \sum_{f \in \text{map}^{-1}(e)} y_f,
-\end{align}
-and the relative load is defined as 
-\begin{align}
-rload(e) = \dfrac{load(e)}{x_e}.
-\end{align}
-\end{definition}
-
-Figure~\ref{fig:racketree} shows an example R\"{a}cke's tree.
-We see a tree on the left-hand side which corresponds to the graph on the right-hand side.
-Each node is labeled by a number.
-The number indicates the projection of $\mathrm{map}$.
-A node of the tree labeled $1$ corresponds to the node in the graph labeled $1$.
-As you can see, the leaves are in bijection with the nodes of the graph.
-
-In addition, edges in the tree correspond to paths in the graph.
-The bolded edges of the tree map to the bolded edges in the graph.
-The top-most edge in the tree connects nodes $3$ and $5$, and that edge maps to the edge in the graph connecting $3$ and $5$.
-Then the bolded edge in the tree connecting $5$ to $5$ corresponds to the empty path.
-The bolded edge of the tree connecting $5$ to $4$ corresponds to the bolded edge in the graph connecting $4$ and $5$.
-Paths in the tree correspond to paths in the graph.
-
-We also note the capacity of the edge in the tree labeled $y$ is $x_1 + x_2 + x_3$.
-Edge $y$ disconnects the leaves into two groups, $S'$ and the rest.
-$S'$ maps bijectively to $S$.
-$S$ induces a cut on the graph, which cuts edges $x_1$, $x_2$, and $x_3$.
-Therefore, the capacity of $y$ (as defined by R\"{a}cke's trees) is the sum of the capacities of $x_1,x_2,$ and $x_3$.
-
-Another thing to notice is that $load(x_1) = 0$, since $\mathrm{map}^{-1}(x_1) = \emptyset$.
-An immediate consequence, which we can see from the load is that removing an edge with load 0 does not affect the connectivity of the graph.
-At a high level, the load will measure how necessary an edge is for connectivity.
-
-\begin{figure}
-\label{fig:racketree}
-\includegraphics[width=\linewidth]{RackeTree.pdf}
-\caption{A R\"{a}cke's tree example.
-A R\"{a}cke tree on the left maps to a graph on the right.
-The map on vertices is defined by the labelings on the nodes.
-The bolded edges map to the bolded edges.
-Edge $y$ defines a set of leaves $S'$, which defines a cut on the graph, $S$.
-$S$ cuts edges $x_1, x_2,$ and $x_3$; therefore, $y = x_1 + x_2 + x_3$.}
-\end{figure}
+At this point, we direct the reader to Figure 1, which contains a visualization of the above definitions.
 
@@
 For each $i$, if there are $f_i$ units of flow going from $s_i$ to $t_i$ in $G$, we route $f_i$ units of flow in the $T$ from $\mathrm{map}^{-1}(s_i)$ to $\mathrm{map}^{-1}(t_i)$.
-If we are given a multicommodity flow $\{ f_i^T \}$ in $T$, then if we have $f_i^T(e)$ units of flow on edge $e$ in $T$, then we route $f_i^T(e)$ units of flow through the path $\mathrm{map}(e)$ in $G$ (recall that edges in $T$ map to paths in $G$).
+For the other direction of the mapping, suppose we are given a multicommodity flow $\{ f_i^T \}$ in $T$.
+If edge $e \in T$ has $f_i^T(e)$ units of flow, then we route $f_i^T(e)$ units of flow through the path $\mathrm{map}(e)$ in $G$ (recall that edges in $T$ map to paths in $G$).
 
-There are some crucial properties of R\"{a}cke's trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to \cite{racke} for the proofs.
+\begin{figure}
+\label{fig:racketree}
+\includegraphics[width=\linewidth]{RackeTree.pdf}
+\caption{An example of a R\"{a}cke's tree embedding.
+On the left, we have the tree $T$, and on the right, we have the original graph $G$ which is embedded in $T$.
+Nodes of $G$ are labeled from 1 through 5, and the nodes of $T$ are labeled by the nodes of $G$ that they are mapped to.
+Note in particular that the leaves of $T$ contain all the labels from 1 through 5, as there is a bijection between the tree leaves and the graph nodes.
+In addition, observe that multiple nodes of the tree map can map to the same node in the graph.
+For example, four nodes in the tree all map to node 3 in $G$, but we specify that $\mathrm{map}^{-1}(3)$ be the specific leaf node that maps to 3.
+\newline
+\text{ }\hspace{.3in} Consider the edge labeled $y$ in the tree.
+The removal of $y$ separates the leaves of the tree into those that are in $S'$ and those that are not in $S'$.
+The leaves in $S'$ map to the nodes in $S$ in $G$, and so the capacity of $y$ is given by the sum of the capacities of the edges that span the cut $(S,V\setminus S)$.
+These edge capacities are $x_1$, $x_2$, and $x_3$, so the capacity of $y$ is $x_1 + x_2+x_3$.
+\newline
+\text{ }\hspace{.3in} Certain edges are bolded to highlight the effect of $\mathrm{map}$ on edges.
+Since the $\mathrm{map}$ function maps edges in the tree to paths in $G$, we have that the bolded edge from 3 to 5 in the tree maps to the bolded length 1 path from 3 to 5 in the graph.
+The bolded edge from 5 to 5 maps to the empty path of length 0 from 5 to 5 in the graph.
+The bolded edge from 4 to 5 maps to the bolded path of length 1 from 4 to 5 in the graph.}
+\end{figure}
+
+Lastly, we define the distribution $\mathcal{D}$ as the uniform distribution over all possible R\"{a}cke's tree embeddings for a given graph $G$.
+There is a polynomial time algorithm for sampling from this distribution, given in \cite{racke}.
+This distribution $\mathcal{D}$ will be important for describing the SSC algorithm, as the algorithm will sample from it.\\
+
+\noindent \textbf{Additional Details.} For the remainder of this section, we provide a number of definitions and statements regarding R\"{a}cke's trees that will be used to wrap up the analysis of Lemma 5 in Section 6.2.
+They are provided here for the sake of completeness, but the reader may skip this section and refer to it if interested while reading the proof of Lemma 5.
+
+\begin{definition}
+Given a R\"{a}cke's tree, the load on an edge of the graph $e \in E$ is
+\begin{align}
+load(e) &= \sum_{f \in \text{map}^{-1}(e)} y_f,
+\end{align}
+\end{definition}
+We can also define the relative load, $rload(e) = load(e)/x_e$.
+
+We provide intuition behind the definition of load.
+Note that in Figure 1, $load(x_1) = 0$, since $\mathrm{map}^{-1}(x_1) = \emptyset$.
+As an immediate consequence of this, we can see that removing an edge with load 0 does not affect the connectivity of the graph.
+At a high level, the load measures how necessary an edge is for connectivity.
+
+The following lemmas are due to R\"{a}cke, and we state them without proof. Their proofs can be found in \cite{racke}.
 
@@
 \end{lemma}
-
-We refer to $\mathcal{D}$ as the distribution over R\"{a}cke trees with the above properties. In \cite{racke}, there is a polynomial time algorithm for sampling from this distribution.
 

### 2015-05-13 draft.tex
finished up to the end of the gkr section

@@
 We then pull together these concepts in Section 5 to present the approximation algorithm for SSC by Chalermsook et al.
-In Section 6, we analyze the performance of the algorithm.
-In Section 7, we present our own ideas for how the algorithm might be modified to improve its approximation ratio under special circumstances.
+Finally, in Section 6, we analyze the performance of the algorithm.
 
@@
 
-The RoundGKR algorithm is a rounding procedure used to solve the Group Steiner Tree (GST) problem \cite{GKR}. The problem it stated as follows. \\
+The final component we need for the SSC algorithm is the RoundGKR procedure, named for its inventors, Garg, Konjevod, and Ravi \cite{GKR}.
+This is the rounding procedure the algorithm for SSC uses, and we will see that this rounding procedure only works for trees.
+We introduced tree embeddings in the previous section solely because of this fact.
+Originally, RoundGKR was developed for the Group Steiner Tree (GST) problem.
+In order to explain the procedure, we give a brief overview of the problem.
+\\
 
@@
 \begin{quote}
-\textbf{Input}: A tree $T = (V_T, E_T)$ rooted at $r$ where each edge has a nonnegative real value cost $c(e)$, along with a set $\{T_i\}$ where each $T_i \subseteq V_T$.\\
-\textbf{Output}: The minimum cost subtree $H \subseteq T$ with a path from $r$ to $t_i$ for some $t \in T_i$ for all $i$.
+\textbf{Input}: A tree $T = (V_T, E_T)$ rooted at $r$ where each edge has a nonnegative real value cost $c(e)$, along with with a collection of sets $T_i$ where each $T_i \subseteq V_T$.\\
+\textbf{Output}: The minimum cost subtree $H \subseteq T$ with a path from $r$ to $t_i$ for some $t_i \in T_i$ for all $i$.
 \end{quote}
 
-The following integer linear program solves the problem exactly:\\
-GST-ILP:
+The following integer linear program solves the problem exactly:
 \begin{align}
 \min & \sum c(e) y_e  \\
-\text{ s.t } & \sum_{e \in \delta(S)} y_e \geq 1, \text{ where } S_i \subset S, T_i \subset V - S, \delta(S) \text{ is the edges of the $S$ cut }
+\text{ s.t } & \sum_{e \in \delta(S)} y_e \geq 1, \text{ where } S_i \subset S, T_i \subset V - S\\
+&y_e \in \{0,1\}
 \end{align}
+
+Recall that $\delta(S)$ is the set of edges spanning the cut $(S,V_T \setminus S)$.
+This program is almost identical to the program for Survivable Set Connectivity, but with $k$ repalced with 1.
+The argument for why this program works is the same as before; we are minimizing the total cost of the included edges, and we are ensuring with the constraints that there is a path from $r$ to $t_i$ for some $t_i \in T_i$.
 
@@
 The optimum to the linear program will assign fractional values in $[0,1]$ to each $y_e$.
-For any $e$, let $p(e)$ denote its parent edge (if it exists).
+For any $e$, let $p(e)$ denote its parent edge in the tree (if it exists).
 We claim that since our problem is to find a subtree that includes the root $r$, edges that are closer to the root are at least as likely to be included in the subtree than edges farther from the root.
@@
 
-The important property of the algorithm can be summarized in the following lemma, whose proof can be found in \cite{GKR}.
+The most important property of RoundGKR is the following lemma, whose proof can be found in \cite{GKR}.
 
@@
 \label{lem:findpath}
-Suppose that $T = (V_t, E_t)$ support a flow of at least $1$ from $T_i$ to the root $r$ without the edges $F_t$.
-Then the RoundGKR returns a solution with a path in $T$ from $T_i$ to $r$ without using $F_t$ with probability at least $\Omega(\frac{1}{\log n})$.
+Suppose that $T = (V_t, E_t)$ supports a flow of at least $1$ from $T_i$ to the root $r$ without using some set of edges $F_t$.
+Then RoundGKR returns a solution with a path in $T$ from $T_i$ to $r$ without using $F_t$ with probability at least $\Omega(\frac{1}{\log n})$.
 \end{lemma}
-
-We will rely on this lemma heavily.
+%
+%We will rely on this lemma heavily.
 In fact, since we need $\Omega(\frac{k}{\log n})$ edge-disjoint paths, we will argue that if we let $F_t$ be any set of at most $\Omega(\frac{k}{\log n})$ edges, then we still have a path, and therefore, we have $\Omega(\frac{k}{\log n})$ paths.
@@
 This finishes the proof that after running the rounding algorithm, each $(S_i, T_i)$ tuple will have $\Omega(\frac{k}{\log n})$ paths connecting $S_i$ to $T_i$.
-
-\section{Potential Improvements}
-
-There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse.
+%
+%\section{Potential Improvements}
+%
+%There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse.
 In the original algorithm, we must iterate through each $v \in V_T$ and run some RoundGKRrounds on its subtree.
@@
 We could be finding $h$ paths with $O(\log n)$ cost (since running RoundGKR on each subtree makes each edge appear in $O(\log n)$ subtrees).
-
-If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small).
+%
+%If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small).
 We can run the algorithm without looking for the nodes where the flow paths turn.
@@
 The algorithm would be:
-\begin{codebox}
-\li Set $H \leftarrow \emptyset$
-\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
-\li Let $x' \leftarrow x*\frac{4}{k}$. 
-\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
-\li \For $\tau$ rounds \Do
-\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
-\li \For $q = 0, ..., 2\log n$ \Do
-\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
-\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
-\li \If $s$ is $q$-marked \Then
-\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
-\li \For $\tau'$ iterations, \Do
-\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
-\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
-\li return $H$
-\end{codebox}
-The main difference lies in line 8.
+%\begin{codebox}
+%\li Set $H \leftarrow \emptyset$
+%\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
+%\li Let $x' \leftarrow x*\frac{4}{k}$. 
+%\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
+%\li \For $\tau$ rounds \Do
+%\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
+%\li \For $q = 0, ..., 2\log n$ \Do
+%\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
+%\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
+%\li \If $s$ is $q$-marked \Then
+%\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
+%\li \For $\tau'$ iterations, \Do
+%\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
+%\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
+%\li return $H$
+%\end{codebox}
+%The main difference lies in line 8.
 Instead of iterating through all $v \in V_T$ to find where the flow path turns, we take advantage of knowing where the flow begins.
@@
 This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.
-
-Lemma~\ref{lem:connected} still holds. Since we know exactly where the flow paths must start.
-
-\begin{lemma}
-The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
-\end{lemma}
-
-\begin{proof}
-The proof is the same as the proof of Lemma~\ref{lem:cost}.
+%
+%Lemma~\ref{lem:connected} still holds. Since we know exactly where the flow paths must start.
+%
+%\begin{lemma}
+%The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
+%\end{lemma}
+%
+%\begin{proof}
+%The proof is the same as the proof of Lemma~\ref{lem:cost}.
 The only difference is that instead of each edge being included in at most $height(T)$ RoundGKR steps, we include it in at most $S$ RoundGKR steps.
-\end{proof}
-
-Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
+%\end{proof}
+%
+%Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
 Along similar lines, if $\sum_{i \in [h]} |T_i| = T$ is small, then we could compress the R\"{a}cke tree to contain only the leaves we want.
@@
 This means we could reduce $\tau'$ to $O(\log \log n)$ and decrease our approximation ratio.
-
-Now the question becomes, can we reduce $S$ to $h$?
+%
+%Now the question becomes, can we reduce $S$ to $h$?
 One possible idea is to join all the nodes in $S_i'$.

### 2015-05-13 draft.tex
finished algorithm description section

@@
 
-Now we will combine the ideas of the linear program to approximate a solution to Survivable Set Connectivity.
-We copy the algorithm as it is written in the paper below, although we will separate the algorithm into parts and explain each part in detail.
+In this section, we present the approximation algorithm given by Chalermsook et al \cite{ssc}. The algorithm uses many concepts presented earlier in the paper, which we remind the reader of first.
+
+The algorithm takes as input a graph $G = (V,E)$ with edge cost function $c$ and $h$ tuples of the form $(S_i,T_i)$ along with a value $k$.
+The algorithm outputs a subgraph $H \subseteq G$, represented as a set of edges of $G$, such that there are at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths between $S_i$ and $T_i$ for each $i$.
+Recall that $k$ edge-disjoint paths was the goal, so we fall short of this requirement by a logarithmic factor.
+The cost of $H$, equal to the sum of the edge costs in $H$, is within a polylogarithmic factor of the optimum.
+
+Recall that SSC-LP is the linear programming relaxation of the ILP for SSC, presented in Section 2.
+Also, $\mathcal{D}$ is the distribution over all possible R\"{a}cke's tree embeddings for a graph $G$, which we can sample from in polynomial time.
+In the algorithm, we use the variable $\tau$ set to be $\log(h)+k$, $\tau'$, set to be $O(\log n)$, and $q$ as an index.
+
+The algorithm is as follows.
+
 \begin{codebox}
@@
 \li Let $x' \leftarrow x*\frac{4}{k}$. 
-\li Prepare $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
+\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
 \li \For $\tau$ rounds \Do
@@
 
-Here, we provide an intuitive explanation of the algorithm as well as the main motivations for each procedure. Of course, we will revist these ideas in the analysis.
+Here, we provide an intuitive explanation of the algorithm as well as the main motivations for each procedure. Of course, we will revisit these ideas in the analysis.
 
-After running the linear program, we rescale $x$ to $x'$ by a $\frac{4}{k}$ factor, which ensures that we have a flow of at least $4$ in each $(S_i, T_i)$.
-This flow of $4$ will correspond to a flow of $4$ in the R\"{a}cke's trees.
+The algorithm first solves the linear programming relaxation, which produces a value of $x_e \in [0,1]$ for each edge $e \in E$.
+The first step is to zero out all values of $x_e < \frac{k}{n^2}$.
+After this, the values are scaled down from $x$ to $x'$ by a $\frac{4}{k}$ factor.
+Since the linear progrom ensures a fractional path of total capacity $k$ from $S_i$ to $T_i$ for each $i$, this $4/k$ scaling ensures a fractional paths of total capacity $4$.
+Since we argued that a flow in the original graph $G$ corresponds to a flow of the same value in any corresponding R\"{a}cke's tree, the resulting tree embeddings will also have flows of value 4.
 
-The RoundGKR algorithm is the main tool used for our rounding scheme.
-RoundGKR finds paths in trees which avoid specific edges with probability $\Omega(\frac{1}{\log n})$ (this is Lemma~\ref{lem:findpath}) given there is sufficient flow.
-We repeat this $\tau' = O(\log n)$ times to assure a constant probability of finding such paths.
+The next step, which the algorithm repeats $\tau = \log(h) + k$ times, begins by sampling a random R\"{a}cke's tree embedding for the graph $G$.
+Then, we create an index $q$ which scrolls from 0 to $2\log n$.
+For each vertex of the tree embedding, and for all possible values of the index $q$, we perform an operation called $q$-marking.
+This simply involves labeling each vertex with the values of $q$ that we $q$-mark it with.
+Therefore, any given vertex can be $q$-marked up to $2\log n + 1$ times.
+For each value of $q$, we $q$-mark a given vertex with probability $\min\{1, \dfrac{4}{2^q}\}$.
+Then for each vertex $v \in E_T$, we go through all values of $q$ such that $v$ was $q$-marked and perform the following steps: 1) Create a new capacity function $y^{v,q}$ that is the original capacity function $y$ for the tree embedding, scaled up by a factor of $2^{q+1}$.
+2) Initialize the set $E^{v,q}$ to be empty.
+3) For $\tau' = O(\log n)$ iterations, run the RoundGKR procedure on the R\"{a}cke's tree, with the given capacity function $y^{v,q}$.
+Whenever edges are output by the procedure, we add them to $E^{v,q}$.
 
-However, we can only run RoundGKR on trees, not general graphs.
-We introduce the R\"{a}cke's tree embedding specifically for this purpose.
-We know a flow of $4$ exists between leaves (Lemma~\ref{lem:mapflows}).
-Each flow path will go up the tree to some ancestor $v$ and then back down to a leaf.
-One such path might be found when $v$ gets marked.
-One path will go to $s_i'$ and one to $t_i'$.
+The purpose of these scaling constants is to ensure that the RoundGKR procedure, which looks for paths of value 1, will actually see these paths.
+We preserve the fact that paths with low capacity are chosen with lower probability.
+The reason why we have $\tau' = O(\log n)$ iterations is because is because  Lemma~\ref{lem:findpath} shows that RoundGKR finds paths in trees which avoid specific edges with probability $\Omega(\frac{1}{\log n})$.
+$O(\log n)$ repetitions ensure a constant probability of finding such paths.
 
-Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoiding some edges.
+Finally, the algorithm concludes by spitting out all of the edges ever returned by any RoundGKR procedure run on any of the iterations for any of the values of $q$ for any of the nodes $v$ that are $q$-marked.
+%
+%Lemma~\ref{lem:findpath} requires us to have a flow of at least $1$ avoiding some edges.
 If a flow path from $s_i'$ to $t_i'$ goes through ancestor $v$ and carries a flow of value $f$, we can apply the lemma if $f \geq 1$.

### 2015-05-13 draft.tex
finished to end of claim a

@@
 The reason why we have $\tau' = O(\log n)$ iterations is because is because  Lemma~\ref{lem:findpath} shows that RoundGKR finds paths in trees which avoid specific edges with probability $\Omega(\frac{1}{\log n})$.
-$O(\log n)$ repetitions ensure a constant probability of finding such paths.
+$O(\log n)$ repetitions ensure a constant probability of finding such paths.t
 
@@
 
+Observe that $c(x)$ is the value of the LP-optimum, which must be at least as good as the true optimum of the problem.
+Therefore, this lemma shows that the cost of the algorithm's solution is within an $O(\log^4n(\frac{\log h}{k}+1))$ factor of the optimum.
+
 \begin{proof}
@@
 
-Let $(T = (V_t, E_t), y, \text{map})$ be a R\"{a}cke's tree sampled from $\mathcal{D}$.
+Let $(T = (V_T, E_T), y, \text{map})$ be a R\"{a}cke's tree sampled from $\mathcal{D}$.
 For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_t$ and some index $q \in [0,\dots,2\log n]$.
@@
 
-For a given edge $e'$, there are at most $height(T)$ ancestors, which means that there are at most $height(T)$ different vertices $v$ that, if $q$-marked, may lead to $e'$ being included.
+We first bound the probability that an edge $e' \in E_T$ is included, which we will then use to bound the probability the algorithm includes an edge $e \in E$.
+
+For a given edge $e' \in E_T$, there are at most $height(T)$ ancestors, which means that there are at most $height(T)$ different vertices $v$ that, if $q$-marked, may lead to $e'$ being included.
 For each $v$, we must consider all $O(\log n)$ possible values of $q$.
@@
 \end{align}
-where the expectation $\text{E}_{R}[X_e]$ is over the random choices of the algorithm, after choosing a R\"{a}cke tree.
+where the expectation $\text{E}_{R}[X_e]$ is over the random choices of the algorithm, after choosing a R\"{a}cke's tree.
 The $\tau$ comes from a union bound over all trials.
@@
 
-To simplify this inequality, we apply a series of definitions and lemmas stated earlier in Section~\ref{sec:rackestrees}. 
+The remainder of this proof relies heavily on the definitions and lemmas stated at the end of Section 3.
+We apply those results in order to simplify the inequality we have above and get our final result.
+We first take the expectation over the random choice of drawing a R\"{a}cke's tree from the distribution $\mathcal{D}$.
+This gives
 \begin{align}
 \textbf{E}_{\mathcal{D}}[E_{R}[X_e]] &\leq \textbf{E}_{\mathcal{D}}[\tau \sum_{e' \in \mathrm{map}^{-1}(e)} O(\log^3 n) y_{e'}] \\
-               &\leq O(\log^3 n) \tau \textbf{E}_{\mathcal{D}}[\sum_{e' \in \mathrm{map}^{-1}(e)} y_{e'}] \\
-               & \leq O(\log^3 n) \tau \textbf{E}_{\mathcal{D}}[load(e)]
+               &\leq O(\log^3 n) \tau \textbf{E}_{\mathcal{D}}[\sum_{e' \in \mathrm{map}^{-1}(e)} y_{e'}]
 \end{align}
-where the expectation is over the choice of R\"{a}cke tree. Using the definition of $rload$, 
+
+Recall that in Section 3, we defined $load(e) = \sum_{e' \in \mathrm{map}^{-1}(e)} y_{e'}$ and $rload(e) = load(e)/x_e$. We thus rewrite the inequality as
 \begin{align}
-\textbf{E}[X_e] &\leq O(\log^3 n) \tau E[rload(e) x_e'] \\
+              \textbf{E}_{\mathcal{D}}[E_{R}[X_e]]  & \leq O(\log^3 n) \tau \textbf{E}_{\mathcal{D}}[load(e)]\\
+&\leq O(\log^3 n) \tau E[rload(e) x_e'] \\
                 &\leq O(\log^3 n) \tau \frac{4}{k} \alpha x_e
 \end{align}
-where $\text{E}[X_e]$ is the expectation over both random choices of the algorithm as well as random choices of the R\"{a}cke tree.
-Lemma~\ref{lem:rload} gives a bound on the maximum relative load.
-$\alpha$ is bounded by $O( \log n)$, so our final inequality is
+The last line of the above computation follows from Lemma 2, which gives a bound on the value of $rload(e)$.
+To simplify notation, we write $\text{E}[X_e]$ as the expectation over both random choices of the algorithm as well as random choices of the R\"{a}cke tree.
+So our final inequality is
 \begin{align}

### 2015-05-13 draft.tex
finished to the end of lemma 6

@@
 
-Lastly, we define the distribution $\mathcal{D}$ as the uniform distribution over all possible R\"{a}cke's tree embeddings for a given graph $G$.
+We define the distribution $\mathcal{D}$ as the uniform distribution over all possible R\"{a}cke's tree embeddings for a given graph $G$.
 There is a polynomial time algorithm for sampling from this distribution, given in \cite{racke}.
@@
 
-\noindent \textbf{Additional Details.} For the remainder of this section, we provide a number of definitions and statements regarding R\"{a}cke's trees that will be used to wrap up the analysis of Lemma 5 in Section 6.2.
-They are provided here for the sake of completeness, but the reader may skip this section and refer to it if interested while reading the proof of Lemma 5.
+Lastly, we introduce the idea of load.
 
@@
 At a high level, the load measures how necessary an edge is for connectivity.
+\noindent \textbf{Additional Details.} For the remainder of this section, we provide a number of statements regarding R\"{a}cke's trees that will be applied to complete the analysis of the algorithm in Section 6.
+They are provided here for the sake of completeness, but the reader may skip this section and refer to it if interested while reading the proofs in Section 6.
 
@@
 \end{align}
-where the expectation $\text{E}_{R}[X_e]$ is over the random choices of the algorithm, after choosing a R\"{a}cke's tree.
+where the expectation $\textbf{E}_{R}[X_e]$ is over the random choices of the algorithm, after choosing a R\"{a}cke's tree.
 The $\tau$ comes from a union bound over all trials.
@@
               \textbf{E}_{\mathcal{D}}[E_{R}[X_e]]  & \leq O(\log^3 n) \tau \textbf{E}_{\mathcal{D}}[load(e)]\\
-&\leq O(\log^3 n) \tau E[rload(e) x_e'] \\
+&\leq O(\log^3 n) \tau \textbf{E}[rload(e) x_e'] \\
                 &\leq O(\log^3 n) \tau \frac{4}{k} \alpha x_e
 \end{align}
-The last line of the above computation follows from Lemma 2, which gives a bound on the value of $rload(e)$.
-To simplify notation, we write $\text{E}[X_e]$ as the expectation over both random choices of the algorithm as well as random choices of the R\"{a}cke tree.
+The last line of the above computation uses the value of $\alpha$, defined in Section 3 as $\alpha = max_{e \in E}\textbf{E}[rload(e)]$.
+We have from Lemma 2 that $\alpha$ is $O(\log n)$.
+To simplify notation, we write $\textbf{E}[X_e]$ as the expectation over both random choices of the algorithm as well as random choices of the R\"{a}cke tree.
 So our final inequality is
@@
 \end{proof}
-
-\begin{figure}
-\label{fig:roundgkronnode}
-\centering
-\includegraphics[width=0.6\linewidth]{RoundGKRonNode.pdf}
-\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
-\end{figure}
+%
+%\begin{figure}
+%\label{fig:roundgkronnode}
+%\centering
+%\includegraphics[width=0.6\linewidth]{RoundGKRonNode.pdf}
+%\caption{Execution of GKR on some subtree rooted at $v$ in a particular round finding paths to $s_i$ and $t_i$.}
+%\end{figure}
 
 Having established that the expected cost is only a polylogarithmic factor away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.
-We will need the following definition.
+We prove this in the next section.
 
@@
 
+First, we define a notion of \emph{good} and \emph{bad} tree embeddings with respect to a subset of edges $F \subseteq E$.
+
 \begin{definition}
-For some set of edges $F \subseteq E$, the sampled tree embedding, $(T, y, \text{map})$ is bad if $F_T = \text{map}^{-1}(F)$ 
+For a set of edges $F \subseteq E$, let $F_T = \text{map}^{-1}(F)$. Then a R\"{a}cke's tree embedding is bad for $F$ if 
 \[ \sum_{e' \in F_T} y_{e'} \geq \frac{1}{2} \]
@@
 
-Intuitively, bad sets correspond to sets which are necessary in the graph.
-We want graphs to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity even if we remove them.
+Intuitively, if a tree embedding is bad with respect to a set $F$, then $F$ is necessary for connectivity in the graph.
+For our argument, we will want tree embeddings to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity even if these sets are removed.
 
@@
 \begin{proof}
-Suppose we have a bad embedding for the set $F$. Then 
+Suppose we have a bad embedding for the set $F$. Using the definition of load, we write
 \begin{align}
@@
 \end{align}
-Where the first inequality we get from taking the sum over the union versus the disjoint union, and the second inequality from the assumption that the tree embedding is bad.
+where the first inequality arises from comparing a sum over a union to a sum over a disjoint union (summands in the first line are counted at least as many times as summnds on the second line), and the second inequality from the assumption that the tree embedding is bad for F.
 
-Therefore, a bad tree means that the load of the set of $F$ is more than $\frac{1}{2}$. Therefore,
+Therefore, a bad tree means that the load of the set of $F$ (shorthand for the sum of the loads of the edges in $F$) is more than $\frac{1}{2}$. Therefore,
 \begin{align}
@@
 \end{align}
-Since we limited the size of $F$. Now invoking Markov's inequality, we know that the probability of bad event is at most $\frac{1}{2}$. 
+where the last inequality comes from our assumption about the size of $F$.
+Invoking Markov's inequality, the probability that the sum of the loads exceeds $1/2$ is at most $1/2$, so the probability of a bad event is at most $\frac{1}{2}$.
 \end{proof}
@@
 Each flow path must go up the tree to some common ancestor $v$ and then back down.
-\item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
+\item Then we will claim that some $v$ gets $q$-marked for some $q$ and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
 \item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 

### 2015-05-13 draft.tex
Started making changes to last section

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
 
@@
 
-\begin{lemma}[\cite{ssc}]
-\label{lem:connected}
+Now, we can state the theorem we need for the desired connectivity claim.
+Note that since $\alpha = O(\log n)$, the following result says that between each $S_i$ and $T_i$, we have $\Omega(\frac{k}{\log n})$ paths.
+
+\begin{theorem}[\cite{ssc}]
+\label{theorem:connected}
 With probability at least $\frac{3}{4}$, all set pairs are at least $\frac{k}{16\alpha} + 1$ edge connected in $H$. 
-\end{lemma}
+\end{theorem}
 
-\textbf{Proof Idea of Lemma~\ref{lem:connected}}:
+As the proof of this theorem is complicated, we break up the overall structure of the theorem into five parts.
+
+\textbf{Proof Structure for Theorem~\ref{theorem:connected}}:
 \begin{enumerate}
-\item Set a particular set of edges $F$ of size at most $\Omega(\dfrac{k}{\log n})$. 
+\item Select a particular set of edges $F \subseteq E$ of size at most $\Omega(\dfrac{k}{\log n})$. 
 \item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. (This is Lemma~\ref{lem:notbad}). 
-\item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$.
+\item Condition on this probability to show that if we remove $\text{map}(F)$ from the tree, we still have sufficient flow from each $S_i$ to $T_i$.
 Each flow path must go up the tree to some common ancestor $v$ and then back down.
-\item Then we will claim that some $v$ gets $q$-marked for some $q$ and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
+\item Then we will claim that some $v$ gets $q$-marked for some $q$ and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $S_i$ and $T_i$, and so the path will be included with sufficient probability and exclude $F$.
 \item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
@@
 It remains to show that the probability that we find a path from $S_i$ to $T_i$ without using the edges from $F$ is at least $\beta$. We do this in the following lemma.
-\end{proof}
 
@@
 This finishes the proof that after running the rounding algorithm, each $(S_i, T_i)$ tuple will have $\Omega(\frac{k}{\log n})$ paths connecting $S_i$ to $T_i$.
+
+\end{proof}
+
 %

### 2015-05-13 draft.tex
finished all major edits

@@
 
-As the proof of this theorem is complicated, we break up the overall structure of the theorem into five parts.
+As the proof of this theorem is complicated, we break up the overall structure of the proof into five parts.
 
@@
 \begin{enumerate}
-\item Select a particular set of edges $F \subseteq E$ of size at most $\Omega(\dfrac{k}{\log n})$. 
-\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. (This is Lemma~\ref{lem:notbad}). 
-\item Condition on this probability to show that if we remove $\text{map}(F)$ from the tree, we still have sufficient flow from each $S_i$ to $T_i$.
-Each flow path must go up the tree to some common ancestor $v$ and then back down.
-\item Then we will claim that some $v$ gets $q$-marked for some $q$ and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $S_i$ and $T_i$, and so the path will be included with sufficient probability and exclude $F$.
-\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
+\item Fix a particular set of edges $F \subseteq E$ of size at most $\frac{k}{16\alpha} = \Omega(\frac{k}{\log n})$. 
+\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for graph connectivity by claiming that the total $load$ on the edges in low.
+(This is Lemma~\ref{lem:notbad}).
+\item Condition on the event of $F$ not being necessary to show that if we remove $\text{map}(F)$ from the tree, we still have sufficient flow from each $S_i$ to $T_i$.
+Note that any flow paths in the tree must go up the tree to some common ancestor $v$ and then back down.
+Think of these nodes $v$ as ``turning points".
+\item Claim that any turning point $v$ will get $q$-marked for some $q$ and so the RoundGKR algorithm which is rooted at $v$ (recall that we run iterations of the RoundGKR algorithm for any node $v$ that gets $q$-marked) finds a path from $v$ to $S_i$ and from $v$ to $T_i$.
+We show that this path is found with sufficient probability.
+\item We union bound over all possible choices of $F$ and over all $i$ to show that we succeed with constant probability.
+From this, we conclude that removing any set of size $\frac{k}{16 \alpha}$ does not damage connectivity for any of the $(S_i,T_i)$ pairs, so each pair must be at least $\frac{k}{16\alpha} + 1$-connected.
 \end{enumerate}
 
-\begin{proof}[Proof of Lemma~\ref{lem:connected}]
+\begin{proof}[Proof of Theorem~\ref{theorem:connected}]
+
+Step 1 is a trivial set-up step, and step 2 was Lemma 6~\ref{lem:notbad}. Here, we give the details of step 5.
+
 We fix an $F$ of size at most $\frac{k}{16\alpha}$ and an $i$ and show that $(S_i, T_i)$ are connected with an edge outside of $F$.
-I will show this happens with a probability at least $\beta$.
+We show this happens with a probability at least $\beta$, which will be some constant greater than 0.
 So the probability of failure is $(1-\beta)$.
 If we repeat this $\tau = \frac{1}{\beta}\ln(4hn^{\frac{k}{16\alpha}}) = O(\log h + k)$ times, then our failure probability goes down to $\dfrac{1}{4hn^{\frac{k}{16\alpha}}}$.
-So now we take the union bound over all of $F$ and over all $i$, so we get probability of failure at most $\frac{1}{4}$.
+So we take the union bound over all of $F$ and over all $i$, so we get probability of failure at most $\frac{1}{4}$.
 
@@
 
-As of right now, we have shown steps $1$, $2$ and $5$ in the proof idea of Lemma~\ref{lem:connected}. We finish the proof by showing steps $3$ and $4$.
+(As of this point, it remains to show steps 3 and 4, which we do below.)
 
@@
 \begin{proof}
-We condition on the probability that $F$ is good at round $t$, which by Lemma~\ref{lem:notbad} is at least $\frac{1}{2}$.
-Now we can set the $y$ terms of $F_T = \text{map}^{-1}(F)$ to zero, in order to avoid picking an edge in $F$.
 
-Since we have a good embedding with respect to $F$.
-The assumption was that $G$ can support a flow of at least $k$ in the original graph (by the solution to the fractional linear program).
-Recall that we reweighed the values $x$ by $\frac{4}{k}$, so we can support a flow of at least $4$ in the original graph with $x'$.
-So by Lemma~\ref{lem:mapflows}, $T$ supports a flow from $S_i' = \text{map}^{-1}(S_i)$ to $T_i' = \text{map}^{-1}(T_i)$ of value at least $4$.
+For this lemma, we give a very extensive proof sketch. The goal is to convince the reader that this claim is true, but since the proof is incredibly detail heavy, we will gloss over some minor points.
 
-Removing the total capacity of $\frac{1}{2}$, we are left with a flow of $2 - \frac{1}{2} = \frac{3}{2}$.
+We condition on the probability that a sampled tree embedding is good with respect to $F$ at round $t$, which by Lemma~\ref{lem:notbad} is at least $\frac{1}{2}$.
+Now, set the edge capacities $y$ for edges in $F_T = \text{map}^{-1}(F)$ to be zero in order to avoid picking edges in $F$.
+
+Note that since we start with a solution to the fractional LP, we assume that $G$ supports a flow of at least $k$.
+Recall that we reweighed the edge capacities $x$ by $\frac{4}{k}$, so we can support a flow of at least $4$ in the original graph with edge capacities $x'$.
+By Lemma~\ref{lem:mapflows}, any R\"{a}cke's tree embedding for $G$ will supports a flow from $S_i' = \text{map}^{-1}(S_i)$ to $T_i' = \text{map}^{-1}(T_i)$ of value at least $4$.
+
+Removing $F$ from the graph removes a total capacity of at most $\frac{1}{2}$, and so we are left with a flow of at least $4 - \frac{1}{2} > \frac{3}{2}$.
 In particular, we can support a unit flow from $S_i'$ to $T_i'$.
-That unit flow can be decomposed into paths $P_1, ..., P_z$, disregarding paths with very small amount of flow $(\leq \frac{1}{2n^2})$.
+That unit flow can be decomposed into paths $P_1, ..., P_z$ (disregard paths with very small amounts of flow $(\leq \frac{1}{2n^2})$).
 Each flow path goes up from a leaf, turns at some $v$, and then goes down to another leaf.
-Let $\phi_v$ be the flow turning at $v$.
-Let $\phi_v$ be the total flow turning at node $v$.
+Let $\phi_v$ be the total amount of flow from $S_i'$ to $T_i'$ turning at $v$.
 
-Since we support a flow of at least $\frac{3}{2}$ and we removed paths with at most $\frac{1}{2n^2}$ flow, we are left with
-\[ \sum_{v \in V_t} \phi_v \geq \frac{3}{2} - \dfrac{1}{2n^2}|E_t| \geq 1 \]
-Now $\phi_v$ falls between some $(2^{-q_v-1}, 2^{-q_v}]$ for some $q_v \in \{0, ..., 2\log_2 n\}$.
-Now the probability that none of the $v \in V_t$ is $q$-marked exactly at $q_v$ when we have a good embedding is at most $e^{-3/4}$ which follows by a Chernoff bound.
+Since we support a flow of at least $\frac{3}{2}$ and we removed paths with at most $\frac{1}{2n^2}$ flow, we are left with $\sum_{v \in V_t} \phi_v \geq \frac{3}{2} - \dfrac{1}{2n^2}|E_t| \geq 1$ units of flow.
+
+Now since $\phi_v$ is between $\frac{1}{2n^2}$ and 1, it falls between some $(2^{-q_v-1}, 2^{-q_v}]$ for some $q_v \in \{0, ..., 2\log_2 n\}$.
+The probability that none of the $v \in V_T$ are $q$-marked exactly at $q_v$ when we have a good embedding is at most $e^{-3/4}$ (which can be proven by a Chernoff bound).
 The important thing to note is that each time we try to $q$-mark a node, it is an independent event.
@@
 
-Conditioning on finding one such $v$, the path gets multiplied by $2^{q_v+1}$.
-Now it supports a flow of $1$.
+Conditioning on finding one such $v$, the path gets multiplied by $2^{q_v+1}$ (due to construction of the algorithm).
+After the scaling, it supports a flow of $1$.
 Lemma~\ref{lem:findpath} says the path will be included with probability at least $\Omega(\frac{1}{\log n})$ in a single round of RoundGKR.
@@
 
-This concludes steps $3$ and $4$ of the proof idea for Lemma~\ref{lem:connectivity}.
+This concludes steps $3$ and $4$ of the proof idea.
 This finishes the proof that after running the rounding algorithm, each $(S_i, T_i)$ tuple will have $\Omega(\frac{k}{\log n})$ paths connecting $S_i$ to $T_i$.
@@
 
-%
-%\section{Potential Improvements}
-%
-%There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse.
+\section{Conclusion}
+
+In this paper, we introduced the Survivable Set Connectivity problem along with the only known approximation algorithm for it.
+To present the algorithm, we formulated a linear program for the problem, gave a type of tree embedding for general graphs, and a rounding procedure that works exclusively on trees.
+
+It seems that there is much work for improving the algorithm, which currently has a $\log^4(n)$ term in the approximation ratio.
+In an optional section following this conclusion, we give some of our own ideas for potential improvements.
+We were able to shave one of the $\log(n)$ factors in a very special case, but we did not think that our improvements were substantial enough to deserve a large section in this paper.
+
+\section{Optional Section: Minor Potential Improvements}
+
+To Prof.
+Karger: This section is completely optional, and not part of our paper.
+As a group, we were leaning towards not including it at all, but we wanted to show that we had thought about the algorithm deeply outside of just rewriting it.
+
+There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse.
 In the original algorithm, we must iterate through each $v \in V_T$ and run some RoundGKRrounds on its subtree.
@@
 We could be finding $h$ paths with $O(\log n)$ cost (since running RoundGKR on each subtree makes each edge appear in $O(\log n)$ subtrees).
-%
-%If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small).
+
+If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small).
 We can run the algorithm without looking for the nodes where the flow paths turn.
@@
 The algorithm would be:
-%\begin{codebox}
-%\li Set $H \leftarrow \emptyset$
-%\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
-%\li Let $x' \leftarrow x*\frac{4}{k}$. 
-%\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
-%\li \For $\tau$ rounds \Do
-%\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
-%\li \For $q = 0, ..., 2\log n$ \Do
-%\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
-%\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
-%\li \If $s$ is $q$-marked \Then
-%\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
-%\li \For $\tau'$ iterations, \Do
-%\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
-%\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
-%\li return $H$
-%\end{codebox}
-%The main difference lies in line 8.
+\begin{codebox}
+\li Set $H \leftarrow \emptyset$
+\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
+\li Let $x' \leftarrow x*\frac{4}{k}$. 
+\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
+\li \For $\tau$ rounds \Do
+\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
+\li \For $q = 0, ..., 2\log n$ \Do
+\end{codebox}
+\begin{codebox*}
+\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
+\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
+\li \If $s$ is $q$-marked \Then
+\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
+\li \For $\tau'$ iterations, \Do
+\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
+\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
+\li return $H$
+\end{codebox*}
+The main difference lies in line 8.
 Instead of iterating through all $v \in V_T$ to find where the flow path turns, we take advantage of knowing where the flow begins.
@@
 This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.
-%
-%Lemma~\ref{lem:connected} still holds. Since we know exactly where the flow paths must start.
-%
-%\begin{lemma}
-%The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
-%\end{lemma}
-%
-%\begin{proof}
-%The proof is the same as the proof of Lemma~\ref{lem:cost}.
+
+Theorem~\ref{theorem:connected} still holds since we know exactly where the flow paths must start.
+
+\begin{lemma}
+The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
+\end{lemma}
+
+\begin{proof}
+The proof is the same as the proof of Lemma~\ref{lem:cost}.
 The only difference is that instead of each edge being included in at most $height(T)$ RoundGKR steps, we include it in at most $S$ RoundGKR steps.
-%\end{proof}
-%
-%Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
+\end{proof}
+
+Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
 Along similar lines, if $\sum_{i \in [h]} |T_i| = T$ is small, then we could compress the R\"{a}cke tree to contain only the leaves we want.
@@
 This means we could reduce $\tau'$ to $O(\log \log n)$ and decrease our approximation ratio.
-%
-%Now the question becomes, can we reduce $S$ to $h$?
+
+Now the question becomes, can we reduce $S$ to $h$?
 One possible idea is to join all the nodes in $S_i'$.

### 2015-05-13 draft.tex
changed typos

@@
 At a high level, the load measures how necessary an edge is for connectivity.
+\\
 \noindent \textbf{Additional Details.} For the remainder of this section, we provide a number of statements regarding R\"{a}cke's trees that will be applied to complete the analysis of the algorithm in Section 6.
@@
 Recall that $\delta(S)$ is the set of edges spanning the cut $(S,V_T \setminus S)$.
-This program is almost identical to the program for Survivable Set Connectivity, but with $k$ repalced with 1.
+This program is almost identical to the program for Survivable Set Connectivity, but with $k$ replaced with 1.
 The argument for why this program works is the same as before; we are minimizing the total cost of the included edges, and we are ensuring with the constraints that there is a path from $r$ to $t_i$ for some $t_i \in T_i$.
@@
 In the algorithm, we use the variable $\tau$ set to be $\log(h)+k$, $\tau'$, set to be $O(\log n)$, and $q$ as an index.
-
 The algorithm is as follows.
@@
 After this, the values are scaled down from $x$ to $x'$ by a $\frac{4}{k}$ factor.
-Since the linear progrom ensures a fractional path of total capacity $k$ from $S_i$ to $T_i$ for each $i$, this $4/k$ scaling ensures a fractional paths of total capacity $4$.
+Since the linear progrom ensures a fractional path of total capacity $k$ from $S_i$ to $T_i$ for each $i$, this $4/k$ scaling ensures fractional paths of total capacity $4$.
 Since we argued that a flow in the original graph $G$ corresponds to a flow of the same value in any corresponding R\"{a}cke's tree, the resulting tree embeddings will also have flows of value 4.
@@
 The reason why we have $\tau' = O(\log n)$ iterations is because is because  Lemma~\ref{lem:findpath} shows that RoundGKR finds paths in trees which avoid specific edges with probability $\Omega(\frac{1}{\log n})$.
-$O(\log n)$ repetitions ensure a constant probability of finding such paths.t
+$O(\log n)$ repetitions ensure a constant probability of finding such paths.
 
@@
 
-Step 1 is a trivial set-up step, and step 2 was Lemma 6~\ref{lem:notbad}. Here, we give the details of step 5.
+Step 1 is a trivial set-up step, and step 2 was Lemma~\ref{lem:notbad}. Here, we give the details of step 5.
 
@@
 
-It seems that there is much work for improving the algorithm, which currently has a $\log^4(n)$ term in the approximation ratio.
+It seems that there is much room for improvements to the algorithm, which currently has a $\log^4(n)$ term in the approximation ratio.
 In an optional section following this conclusion, we give some of our own ideas for potential improvements.
@@
 \li \For $q = 0, ..., 2\log n$ \Do
-\end{codebox}
-\begin{codebox*}
 \li \For \For $i \in [h]$ and $s \in S_i'$ \Do
@@
 \li return $H$
-\end{codebox*}
+\end{codebox}
 The main difference lies in line 8.

### 2015-05-14 draft.tex
fixed all typos

@@
 
-In SSC, the problem is modified so that each pair of sets $(S_i,T_i)$ must be connected by $k_i$ paths, instead of just 1. More formally, the problem is:
+In SSC, the problem is modified so that each pair of sets $(S_i,T_i)$ must be connected by $k$ paths, instead of just 1. More formally, the problem is:
 
@@
 
-We define the distribution $\mathcal{D}$ as the uniform distribution over all possible R\"{a}cke's tree embeddings for a given graph $G$.
+We define the distribution $\mathcal{D}$ as the distribution over R\"{a}cke's tree embeddings for a given graph $G$.
 There is a polynomial time algorithm for sampling from this distribution, given in \cite{racke}.
@@
 
-The following lemmas are due to R\"{a}cke, and we state them without proof. Their proofs can be found in \cite{racke}.
+The following lemmas are due to R\"{a}cke, and we state them without proof. Their proofs can be found in \cite{racke} and \cite{ssc}.
 
@@
 The final component we need for the SSC algorithm is the RoundGKR procedure, named for its inventors, Garg, Konjevod, and Ravi \cite{GKR}.
-This is the rounding procedure the algorithm for SSC uses, and we will see that this rounding procedure only works for trees.
+This is the rounding procedure the algorithm for SSC uses, and we will see that this rounding procedure works for trees.
 We introduced tree embeddings in the previous section solely because of this fact.
@@
 \min & \sum c(e) y_e  \\
-\text{ s.t } & \sum_{e \in \delta(S)} y_e \geq 1, \text{ where } S_i \subset S, T_i \subset V - S\\
+\text{ s.t } & \sum_{e \in \delta(S)} y_e \geq 1, \text{ where } \{ r \} \subset S, T_i \subset V - S\\
 &y_e \in \{0,1\}
@@
 Also, $\mathcal{D}$ is the distribution over all possible R\"{a}cke's tree embeddings for a graph $G$, which we can sample from in polynomial time.
-In the algorithm, we use the variable $\tau$ set to be $\log(h)+k$, $\tau'$, set to be $O(\log n)$, and $q$ as an index.
+In the algorithm, we use the variable $\tau$ set to be $O(\log(h)+k)$, $\tau'$, set to be $O(\log n)$, and $q$ as an index.
 The algorithm is as follows.
@@
 
-The next step, which the algorithm repeats $\tau = \log(h) + k$ times, begins by sampling a random R\"{a}cke's tree embedding for the graph $G$.
+The next step, which the algorithm repeats $\tau = O(\log(h) + k)$ times, begins by sampling a random R\"{a}cke's tree embedding for the graph $G$.
 Then, we create an index $q$ which scrolls from 0 to $2\log n$.
@@
 For each value of $q$, we $q$-mark a given vertex with probability $\min\{1, \dfrac{4}{2^q}\}$.
-Then for each vertex $v \in E_T$, we go through all values of $q$ such that $v$ was $q$-marked and perform the following steps: 1) Create a new capacity function $y^{v,q}$ that is the original capacity function $y$ for the tree embedding, scaled up by a factor of $2^{q+1}$.
-2) Initialize the set $E^{v,q}$ to be empty.
-3) For $\tau' = O(\log n)$ iterations, run the RoundGKR procedure on the R\"{a}cke's tree, with the given capacity function $y^{v,q}$.
+Then for each vertex $v \in V_T$, we go through all values of $q$ such that $v$ was $q$-marked and perform the following steps:
+\begin{enumerate}
+\item Create a new capacity function $y^{v,q}$ that is the original capacity function $y$ for the tree embedding, scaled up by a factor of $2^{q+1}$.
+\item Initialize the set $E^{v,q}$ to be empty. 
+\item For $\tau' = O(\log n)$ iterations, run the RoundGKR procedure on the R\"{a}cke's tree, with the given capacity function $y^{v,q}$.
 Whenever edges are output by the procedure, we add them to $E^{v,q}$.
+\end{enumerate}
 
@@
 Let $(T = (V_T, E_T), y, \text{map})$ be a R\"{a}cke's tree sampled from $\mathcal{D}$.
-For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_t$ and some index $q \in [0,\dots,2\log n]$.
+For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_T$ and some index $q \in [0,\dots,2\log n]$.
 For this to occur, $v$ must be $q$-marked, an event that occurs with probability $\frac{4}{2^{q}}$.
@@
 \end{align}
-The last line of the above computation uses the value of $\alpha$, defined in Section 3 as $\alpha = max_{e \in E}\textbf{E}[rload(e)]$.
+The last line of the above computation uses the value of $\alpha$, defined in Section 3 as $\alpha = \max_{e \in E}\textbf{E}[rload(e)]$.
 We have from Lemma 2 that $\alpha$ is $O(\log n)$.
@@
 In this paper, we introduced the Survivable Set Connectivity problem along with the only known approximation algorithm for it.
-To present the algorithm, we formulated a linear program for the problem, gave a type of tree embedding for general graphs, and a rounding procedure that works exclusively on trees.
+To present the algorithm, we formulated a linear program for the problem, gave a type of tree embedding for general graphs, and a rounding procedure designed to work on trees.
 
-It seems that there is much room for improvements to the algorithm, which currently has a $\log^4(n)$ term in the approximation ratio.
-In an optional section following this conclusion, we give some of our own ideas for potential improvements.
+It seems that there should be room for improvement to the algorithm presented in this paper, which has a $\log^4(n)$ term in the approximation ratio.
+We are optimistic that a better approxiation will be found in the future.
+
+%
+%In an optional section following this conclusion, we give some of our own ideas for potential improvements.
 We were able to shave one of the $\log(n)$ factors in a very special case, but we did not think that our improvements were substantial enough to deserve a large section in this paper.
-
-\section{Optional Section: Minor Potential Improvements}
-
-To Prof.
+%
+%\section{Optional Section: Minor Potential Improvements}
+%
+%To Prof.
 Karger: This section is completely optional, and not part of our paper.
 As a group, we were leaning towards not including it at all, but we wanted to show that we had thought about the algorithm deeply outside of just rewriting it.
-
-There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse.
+%
+%There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse.
 In the original algorithm, we must iterate through each $v \in V_T$ and run some RoundGKRrounds on its subtree.
@@
 This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.
-
-Theorem~\ref{theorem:connected} still holds since we know exactly where the flow paths must start.
-
-\begin{lemma}
-The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
-\end{lemma}
-
-\begin{proof}
-The proof is the same as the proof of Lemma~\ref{lem:cost}.
+%
+%Theorem~\ref{theorem:connected} still holds since we know exactly where the flow paths must start.
+%
+%\begin{lemma}
+%The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
+%\end{lemma}
+%
+%\begin{proof}
+%The proof is the same as the proof of Lemma~\ref{lem:cost}.
 The only difference is that instead of each edge being included in at most $height(T)$ RoundGKR steps, we include it in at most $S$ RoundGKR steps.
-\end{proof}
-
-Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
+%\end{proof}
+%
+%Therefore, if $S = o(\log n)$, it is better to run this modified algorithm.
 Along similar lines, if $\sum_{i \in [h]} |T_i| = T$ is small, then we could compress the R\"{a}cke tree to contain only the leaves we want.
